---
title: "Data Preparation" 
author: "Anna Makova (under supervision of Jacob Bellmund)"
date: "05/08/2021"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
---

# Data Preparation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up

Packages used for data preparation 
```{r libraries}
library(tidyverse)
library(here)
```

Functions writted for this analysis 
```{r functions}
#function angleDiff() takes in 2 angles in degrees and gives out the difference between them (0-180) with the proper direction 
#(i.e. positive = clockwise, negative = counterclockwise; angle1 being theoretical 0/trueAngle)
angleDiff <- function(angle1, angle2){
    x = angle2 - angle1
    if (x > 180) {x = x -360} else if (x < -180) {x = x + 360}
    return(x)
}

#function dist() calculates distance between 2 given points (loc1, loc2) while taking in their X and Y separately
dist <- function(loc1X, loc1Y, loc2X, loc2Y) {
   d = sqrt(((loc1X-loc2X)**2)+((loc1Y-loc2Y)**2))
   return(d)
}

#function angle() takes in 2 locations (a, b) and calculates angle between A-B and A-C (created inside the function)
#a(X, Y) = character position, b(X, Y) = imaginary object position
#necessary for relative influence calculation
angle <- function(a_X, a_Y, b_X, b_Y) { 
  c_X = a_X
  c_Y = a_Y + 10
  c = dist(a_X, a_Y, b_X, b_Y)
  b = dist(a_X, a_Y, c_X, c_Y)
  a = dist(b_X, b_Y, c_X, c_Y)
  cos_A = (b^2 + c^2 - a^2) / (2*b*c)
  angleRad = acos(cos_A)
  angle = (180 * angleRad) / pi 
  if (a_X > b_X) {angle = 360 - angle}
  return(angle)
}
```

Setting up condition of running the chunks below
```{r}
data_here <- nchar(here()) < 50
```


Creating a list of subject IDs based on presence of summary files for Block 4 
Subsequently, creating list of new random IDs which were used during a transfer of data between computers
```{r ID, eval=data_here}
fn <- list.files(path =  here("data"), pattern="*_feedbackPhase_block4_Sum") 
subjects <- c()
for (i_file in length(fn)) {
  subjects <- substr(fn,1,4)
}

newID <- sample(c(1000:9999), size=length(subjects), replace=FALSE)
```

Retrieving participants' age from participants.csv (used for participation tracking purposes, created manually)
```{r age, eval=data_here}
age <- read.table(here("data", "participants.csv"), sep  = ";", header = TRUE, colClasses = "character") %>% 
  select(study.ID, age, study) %>% 
  filter(study == "yes") 
```

## Summary and Angle files 
The files are loaded in and joined into a big data frame containing all information from both summary and angle files for all participants

Dataframes created along the way:

- Sum_all: all participants
- Sum: all data for 1 participant 
- sub_dat: data from 1 block for 1 participant 

```{r Summary, eval=data_here}
blocks <- c(1, 2, 3, 4) #number of blocks in the experiment
Sum_all = tibble() #creating an empty tibble where eventually will the full dataset be stored

for(i_sub in subjects){
  #new, empty tibble for each participant
  Sum = tibble()
  for (i_block in blocks){
    
    #loading in summary data
    fn <- dir(path = here("data"), pattern = sprintf("%s_feedbackPhase_block%s_Sum", i_sub, i_block), full.names = TRUE) 
    sub_dat <- as_tibble(read_delim(fn, delim = "\t", col_names = FALSE, col_types = "dcdddddddddddddd")) %>%
      rename(trial = X1, object = X2, sec2Beg = X3, landmarkX = X4, landmarkZ = X5, landmarkY = X6, objX = X7, objZ = X8, objY = X9, 
             error=X13, secTrialRepl = X14, trialLen = X15, sec2End = X16, remLocX = X10, remLocY = X12, remLocZ = X11) %>% 
      mutate(ID=i_sub, 
             newID=newID[which(subjects == i_sub)], 
             age=age$age[which(i_sub==age$study.ID)], 
             block=i_block, dropTime = (sec2Beg + secTrialRepl), miniblock = NA, objectTrial = NA, cue=NA,
             landmarkCuePosX=NA, landmarkCuePosY=NA, boundaryCuePosX=NA, boundaryCuePosY=NA, relativeInfluence=NA, cueDissonance = NA, 
             angleError=NA, landmarkAngle=NA, boundaryAngle=NA, relativeAngle=NA, cueDissonanceAngle = NA, 
             distanceTo1 = NA, distanceTo2=NA, distanceTo3=NA, averageDist=NA) 
    
    #loading in angle data
    fn_A <- dir(path = here("data"), pattern = sprintf("%s_feedbackPhase_block%s_Angle", i_sub, i_block), full.names = TRUE) 
    sub_dat_A <- as_tibble(read_delim(fn_A, delim = "\t", col_names = FALSE, col_types = "dcdddddddddd")) %>%
      mutate(ID=i_sub, block=i_block) %>% 
      rename(trial = X1, object = X2, charX = X3, charZ = X4, charY = X5, estAngle = X6, objX = X7, objZ = X8, objY = X9, trueAngle = X10,
             secTrialEst = X11, sec2Est = X12) 
  
    #joining together sub_dat and sub_datA
    sub_dat <- inner_join(sub_dat, sub_dat_A, by=c("trial", "object", "objX", "objZ", "objY", "ID", "block"))
    
    #renaming objects in German to English
    sub_dat[sub_dat == "die Lampe"] <- "lamp"
    sub_dat[sub_dat == "die Blume"] <- "flower"
    sub_dat[sub_dat == "der Partyhut"] <- "partyhat"
    sub_dat[sub_dat == "das Monster"] <- "monster"
    
    #assigning miniblocks based on trial number
    for (i_trial in 1:(length(sub_dat$trial))){
      if (sub_dat$trial[i_trial] < 5) {
        sub_dat$miniblock[i_trial] <- 1
      } else if (sub_dat$trial[i_trial] < 9) {
        sub_dat$miniblock[i_trial] <- 2
      } else if (sub_dat$trial[i_trial] < 13) {
        sub_dat$miniblock[i_trial] <- 3 
      } else {
        sub_dat$miniblock[i_trial] <- 4
      }
      
      #assigning objectTrial (1-16) - miniblock order number throughout the experiment
      sub_dat$objectTrial[i_trial] <- (sub_dat$miniblock[i_trial]+((sub_dat$block[i_trial]-1)*4))
      
      
      #finding distance between remembered position and other than target objects
      objects <- c("monster", "partyhat", "lamp", "flower")
      otherObjects <- objects[objects != sub_dat$object[i_trial]]
      sub_dat$distanceTo1[i_trial] <- dist(sub_dat$remLocX[i_trial], sub_dat$remLocY[i_trial], 
                                           sub_dat$objX[sample(which(sub_dat$object == otherObjects[1]),1)],
                                           sub_dat$objY[sample(which(sub_dat$object == otherObjects[1]),1)])
      sub_dat$distanceTo2[i_trial] <- dist(sub_dat$remLocX[i_trial], sub_dat$remLocY[i_trial], 
                                           sub_dat$objX[sample(which(sub_dat$object == otherObjects[2]),1)],
                                           sub_dat$objY[sample(which(sub_dat$object == otherObjects[2]),1)])
      sub_dat$distanceTo3[i_trial] <- dist(sub_dat$remLocX[i_trial], sub_dat$remLocY[i_trial], 
                                           sub_dat$objX[sample(which(sub_dat$object == otherObjects[3]),1)], 
                                           sub_dat$objY[sample(which(sub_dat$object == otherObjects[3]),1)])
      
      #averaging the distance to the other 3 objects' locations to get a single value
      sub_dat$averageDist[i_trial] <- (sub_dat$distanceTo1[i_trial] + sub_dat$distanceTo2[i_trial] + sub_dat$distanceTo3[i_trial])/3
      
      #calculating the angle error 
      sub_dat$angleError[i_trial] <- angleDiff(sub_dat$trueAngle[i_trial], sub_dat$estAngle[i_trial])
    }
    
    Sum <- bind_rows(sub_dat, Sum)  
  }
  
  # JB: START ADAPTED SECTION
  # find names of boundary objects based on X-coordinate (should repeat for boundary)
  boundary_objects <- Sum %>%  
    count(object, objX) %>% # count appearances of each object at given location
    arrange(desc(n)) %>% # sort based on count -> boundary objects are always at same position -> high counts
    slice(c(1,2)) %>% # top two rows should be boundary objects
    pull(object) # extract boundary object names
  
  # find names of landmark objects based on Y-coordinate (should repeat for boundary)
  landmark_objects <- Sum %>%  
    count(object, objY) %>% # count appearances of each object at given location
    arrange(desc(n)) %>% # sort based on count -> boundary objects are always at same position -> high counts
    tail(-2) %>% # top two rows should be boundary objects, exclude them
    distinct(object) %>% # store only unique object names
    pull(object) # extract boundary object names
  
  #assigning boundary- vs landmark-bound 
  Sum <- Sum %>% 
    mutate(cue = case_when(
      object %in% boundary_objects ~ "boundary",
      object %in% landmark_objects ~ "landmark")
    )
  
  # some sanity checks
  if (length(landmark_objects) != 2){stop(sprintf("Did not find exactly 2 landmark objects for subject %s", i_sub))}
  if (length(boundary_objects) != 2){stop(sprintf("Did not find exactly 2 boundary objects for subject %s", i_sub))}
  if(any(is.na(Sum$cue))){stop(sprintf("Did not assign cue for at least one trial for subject %s", i_sub))}
  
  # Check that assignment of landmark or boundary produced the same cue value for each block -> there should be 4 rows, one per object
  if (Sum %>% count(object, cue) %>% nrow() != 4){
    warning(sprintf("Assignment of landmark/boundary cue has gone wrong for subject %s", i_sub))
  }
  # JB: END ADAPTED SECTION 
  
  
  #assigning predicted position based on the cue (boundary vs landmark)
  for (i_trial in 1:nrow(Sum)) {
    
    #block 1
    if (Sum$block[i_trial] == 1){ 
        #not applicable for block 1 as there has not been any movement of the landmark -> all true locations and angles
        Sum$landmarkCuePosX[i_trial] <- Sum$objX[i_trial]
        Sum$landmarkCuePosY[i_trial] <- Sum$objY[i_trial]
        Sum$boundaryCuePosX[i_trial] <- Sum$objX[i_trial]
        Sum$boundaryCuePosY[i_trial] <- Sum$objY[i_trial]
        Sum$landmarkAngle[i_trial] <- Sum$trueAngle[i_trial]
        Sum$boundaryAngle[i_trial] <- Sum$trueAngle[i_trial]
     
    #block 2       
    }else if (Sum$block[i_trial] == 2){ 
      
        #landmark-dependent objects
        if (Sum$cue[i_trial] == "landmark") {
          #position predicted by landmark is the true object position
          Sum$landmarkCuePosX[i_trial] <- Sum$objX[i_trial]
          Sum$landmarkCuePosY[i_trial] <- Sum$objY[i_trial]
          
          #position predicted by boundary is the true object position in block 1
          Sum$boundaryCuePosX[i_trial] <- Sum$objX[sample(which(Sum$block == 1 & Sum$object == Sum$object[i_trial]), 1)]
          Sum$boundaryCuePosY[i_trial] <- Sum$objY[sample(which(Sum$block == 1 & Sum$object == Sum$object[i_trial]), 1)]
          
          #angle predicted by landmark is angle towards the true location 
          Sum$landmarkAngle[i_trial] <- Sum$trueAngle[i_trial]
          
          #angle predicted by boundary is angle towards object position in block 1
          Sum$boundaryAngle[i_trial] <- angle(Sum$charX[i_trial], Sum$charY[i_trial], Sum$boundaryCuePosX[i_trial], Sum$boundaryCuePosY[i_trial])
        
        #boundary-dependent objects  
        } else { 
          #position predicted by boundary is the true object position
          Sum$boundaryCuePosX[i_trial] <- Sum$objX[i_trial]
          Sum$boundaryCuePosY[i_trial] <- Sum$objY[i_trial]
          
          #position predicted by landmark is calculated based on landmark movement
          idx <- which(Sum$objectTrial == 1 & Sum$object == Sum$object[i_trial])
          Sum$landmarkCuePosX[i_trial] <- (Sum$objX[idx] + (Sum$landmarkX[i_trial]-Sum$landmarkX[idx]))
          Sum$landmarkCuePosY[i_trial] <- (Sum$objY[idx] + (Sum$landmarkY[i_trial]-Sum$landmarkY[idx]))
          
          #angle predicted by boundary is angle towards the true location 
          Sum$boundaryAngle[i_trial] <- Sum$trueAngle[i_trial]
          
          #angle predicted by landmark is angle towards the position predicted by landmark 
          Sum$landmarkAngle[i_trial] <- angle(Sum$charX[i_trial], Sum$charY[i_trial] ,Sum$landmarkCuePosX[i_trial], Sum$landmarkCuePosY[i_trial])
        }
    
    #block 3 and 4
    }else{ 
        #landmark-dependent objects
        if (Sum$cue[i_trial] == "landmark") {
          
          # true position and angle 
          Sum$landmarkCuePosX[i_trial] <- Sum$objX[i_trial]
          Sum$landmarkCuePosY[i_trial] <- Sum$objY[i_trial]
          Sum$landmarkAngle[i_trial] <- Sum$trueAngle[i_trial]
          
          #Retrieving coordinates of the object in block 1
          block1BoundaryX <- Sum$objX[sample(which(Sum$block == 1 & Sum$object == Sum$object[i_trial]), 1)]
          block1BoundaryY <- Sum$objY[sample(which(Sum$block == 1 & Sum$object == Sum$object[i_trial]), 1)]
          
          #Retrieving coordinates of the object in previous block
          block2BoundaryX <- Sum$objX[sample(which(Sum$block == (Sum$block[i_trial]-1) & Sum$object == Sum$object[i_trial]), 1)]
          block2BoundaryY <- Sum$objY[sample(which(Sum$block == (Sum$block[i_trial]-1)  & Sum$object == Sum$object[i_trial]), 1)]
          
          #Calculating the distance to the remembered position of the 2 retrieved positions 
          diffBlock1 <- dist(block1BoundaryX, block1BoundaryY, Sum$remLocX[i_trial], Sum$remLocY[i_trial])
          diffBlock2 <- dist(block2BoundaryX, block2BoundaryY, Sum$remLocX[i_trial], Sum$remLocY[i_trial])
          
          #The position that is closer to the remembered position is assigned as the position predicted by boundary
          if (diffBlock1 < diffBlock2) {
            Sum$boundaryCuePosX[i_trial] <- block1BoundaryX
            Sum$boundaryCuePosY[i_trial] <- block1BoundaryY
          } else {
            Sum$boundaryCuePosX[i_trial] <- block2BoundaryX
            Sum$boundaryCuePosY[i_trial] <- block2BoundaryY
          }
          
          #Calculating the angle predicted by boundary based on the position predicted by boundary
          Sum$boundaryAngle[i_trial] <- angle(Sum$charX[i_trial], Sum$charY[i_trial], Sum$boundaryCuePosX[i_trial], Sum$boundaryCuePosY[i_trial])
        
        #boundary-dependent objects
        } else { 
          #true position and angle 
          Sum$boundaryCuePosX[i_trial] <- Sum$objX[i_trial]
          Sum$boundaryCuePosY[i_trial] <- Sum$objY[i_trial]
          Sum$boundaryAngle[i_trial] <- Sum$trueAngle[i_trial]
          
          #Calculating landmark predicted position as if the object was landmark-dependent since block 1
          idx1 <- sample(which(Sum$block == 1 & Sum$object == Sum$object[i_trial]), 1)
          block1LandmarkX <- (Sum$objX[idx1] + (Sum$landmarkX[i_trial]-Sum$landmarkX[idx1]))
          block1LandmarkY <- (Sum$objY[idx1] + (Sum$landmarkY[i_trial]-Sum$landmarkY[idx1]))
          
          #Calculating new position as if the object was landmark-dependent since previous block
          idx2 <- sample(which(Sum$block == (Sum$block[i_trial]-1) & Sum$object == Sum$object[i_trial]), 1)
          block2LandmarkX <- (Sum$objX[idx2] + (Sum$landmarkX[i_trial]-Sum$landmarkX[idx2]))
          block2LandmarkY <- (Sum$objY[idx2] + (Sum$landmarkY[i_trial]-Sum$landmarkY[idx2]))
          
          #Calculating the distance to the remembered position of the 2 calculated positions
          diffBlock1 <- dist(block1LandmarkX, block1LandmarkY, Sum$remLocX[i_trial], Sum$remLocY[i_trial])
          diffBlock2 <- dist(block2LandmarkX, block2LandmarkY, Sum$remLocX[i_trial], Sum$remLocY[i_trial])
          
          #The position that is closer to the remembered position is assigned as the position predicted by landmark
          if (diffBlock1 < diffBlock2) {
            Sum$landmarkCuePosX[i_trial] <- block1LandmarkX
            Sum$landmarkCuePosY[i_trial] <- block1LandmarkY
          } else {
            Sum$landmarkCuePosX[i_trial] <- block2LandmarkX
            Sum$landmarkCuePosY[i_trial] <- block2LandmarkY
          }
          
          #Calculating the angle predicted by landmark based on the position predicted by landmark
          Sum$landmarkAngle[i_trial] <- angle(Sum$charX[i_trial], Sum$charY[i_trial], Sum$landmarkCuePosX[i_trial], Sum$landmarkCuePosY[i_trial])
        }
    } 
    
    #calculating the relative influence of each cue on the remembered location of the cued object
    distL <- dist(Sum$landmarkCuePosX[i_trial], Sum$landmarkCuePosY[i_trial], Sum$remLocX[i_trial], Sum$remLocY[i_trial])
    distB <- dist(Sum$boundaryCuePosX[i_trial], Sum$boundaryCuePosY[i_trial], Sum$remLocX[i_trial], Sum$remLocY[i_trial])
    Sum$relativeInfluence[i_trial] <- distL / (distL + distB)
    
    #calculating the relative influence of each cue on the indicated angle    
    errorL <- abs(angleDiff(Sum$landmarkAngle[i_trial], Sum$estAngle[i_trial]))
    errorB <- abs(angleDiff(Sum$boundaryAngle[i_trial], Sum$estAngle[i_trial]))
    Sum$relativeAngle[i_trial] <- errorL / (errorL + errorB)
    
    #calculating the relative influence with a new formula "distCorrect/(distCorrect+distOther)" and creating values in the same direction for both cues, new variable name - cue dissonance
    if (Sum$cue[i_trial] == "boundary") {
      Sum$cueDissonance[i_trial] <- distB / (distB + distL)
      Sum$cueDissonanceAngle[i_trial] <- errorB / (errorL + errorB)
    } else {
      Sum$cueDissonance[i_trial] <- distL / (distL + distB)
      Sum$cueDissonanceAngle[i_trial] <- errorL / (errorL + errorB)
    }
    
  }
  
  Sum_all <- bind_rows(Sum_all, Sum) #join the new participant data to the existing overall data frame
}
```

Last changes to the dataframe to make it ready for analysis.

```{r, eval=data_here}
#assigning the correct format to values in columns used for analysis
Sum_all <- Sum_all %>% 
  arrange(ID, objectTrial) %>% #ordering the dataframe according to ID and the experiment sequence
  mutate( 
         cueMM = recode(cue, "boundary" = 1, "landmark" = -1), #recoding cues to 1 and -1, used for mixed model analysis
         newID = as.factor(newID), 
         cue = as.factor(cue), 
         age = as.numeric(age)
         ) 

# calculating centered age and miniblock (using this more complicated way as opposed to directly do scale() because different subjects can have a different number of rows in the Sum_all tibble)
Age_c <- Sum_all %>% 
  group_by(ID) %>%
  distinct(age) %>%
  ungroup() %>%
  mutate(age_c = scale(age, center=TRUE, scale=FALSE)) 


Mini_c <- Sum_all %>% 
  group_by(ID) %>%
  distinct(miniblock) %>%
  ungroup() %>%
  mutate(mini = scale(miniblock, center=TRUE, scale=FALSE))

Sum_all <- inner_join(Sum_all, Age_c%>%select(ID, age_c), by="ID")
Sum_all <- inner_join(Sum_all, Mini_c, by=c("ID", "miniblock"))
```

Assigning landmark-dependent/boundary-dependent object 1-2
(currently not used any further)
```{r cue1, eval=FALSE}
Sum_all <- mutate(Sum_all, cue1=NA) #creating new column 

for (i_trial in 1:nrow(Sum_all)) { 
  #if this is the first time participant sees the object
  if (Sum_all$objectTrial[i_trial]==1) {
    #creates a dataframe "this" that has 2 lines (1 line = current object/trial + 1 line = other landmark-/boundary-dependent object)
    this <- filter(Sum_all, ID == Sum_all$ID[i_trial] & cue == Sum_all$cue[i_trial] & objectTrial == 1) %>% 
      select(ID, objectTrial, cue, cue1)
    
    #if the first object has not been assigned number yet, then this object/trial is assigned 1, otherwise 2
    if (is.na(this$cue1[1])) {Sum_all$cue1[i_trial] <- 1} else {Sum_all$cue1[i_trial] <- 2} 
    
  #retrieves and assigns information about object number from objectTrial 1
  } else {
    Sum_all$cue1[i_trial] <- Sum_all$cue1[which(Sum_all$ID == Sum_all$ID[i_trial] & Sum_all$object == Sum_all$object[i_trial] & Sum_all$objectTrial == 1)]
  }
}
```

## Trajectory files

Loading in Trajectory files and creating one huge data frame (~30,000 lines per participant)

```{r Trajectory, eval=data_here}
Traj = tibble() #creating an empty where eventually the full dataframe will be stored (>2M lines)

for(i_sub in subjects){
  for (i_block in blocks){
    #loading in a single trajectory file 
    fn <- dir(path = here("data"), pattern = sprintf("%s_feedbackPhase_block%s_Traj", i_sub, i_block),full.names=TRUE) 
    sub_dat <- as_tibble(read_delim(fn, delim = "\t", col_names = FALSE, col_types = "ddddddddddd")) %>% 
      mutate(ID=i_sub, newID = NA, block=i_block, miniblock = NA, object = NA, cue=NA) %>% 
      rename(trial=X1, sec2Frame=X2, charX=X3, charZ=X4, charY=X5, rotQua1=X6, rotQua2=X7, rotQua3=X8, rotQua4=X9, rotAngle=X10) %>% 
      relocate(ID, newID, block)
    
    #assigning miniblock
    for (i in 1:nrow(sub_dat)){
      if (sub_dat$trial[i] < 5) {
        sub_dat$miniblock[i] <- 1
      } else if (sub_dat$trial[i] < 9) {
        sub_dat$miniblock[i] <- 2
      } else if (sub_dat$trial[i] < 13) {
        sub_dat$miniblock[i] <- 3 
      } else {
        sub_dat$miniblock[i] <- 4
      }
    
      #sub_dat$objectTrial[i] <- (sub_dat$miniblock[i]+((sub_dat$block[i]-1)*4)) Currently not used so taken out for speed
      
      #retrieving information about object and cue from summary file
      obj <- which(Sum_all$ID == sub_dat$ID[i] & Sum_all$block == sub_dat$block[i] & Sum_all$trial == sub_dat$trial[i])
      
      #some trials in summary files missing therefore it leave the columns as NA is it cannot find the above index
      if (length(obj) == 1) {
        sub_dat$object[i] <- Sum_all$object[obj]
        sub_dat$cue[i] <- Sum_all$cue[obj]
        #sub_dat$cue1[i] <- Sum_all$cue1[obj] currently not used
      } 
    }
    #assigning newID
    sub_dat$newID <- newID[which(subjects == i_sub)]
   
    # append to table with data from all subjects
    Traj <- bind_rows(sub_dat, Traj)
  }
}
```

Getting rid of trajectory locations outside of the arena which have been probably caused by an internet glitch 

```{r Traj filtering, eval=data_here}
#removing locations outside of the arena (possibly internet glitch)
Traj <- filter(Traj, charX > -27.5 & charX < 27.5 & charY > -27.5 & charY < 27.5) 
```

## Memory scores

### Based on randomly distributed 1000 locations within the arena

Generating 1000 randomly distributed locations within the arena

```{r thousand points, eval=data_here}
thousand_x <- c()
thousand_y <- c()
points <- c(1:1000)
circle_r <- 22.5 
for (i in points){
  
  # random angle
  alpha <- 2 * pi * runif(1)
  
  # random radius
  r <- circle_r * sqrt(runif(1))
  
  # calculating coordinates
  x <- r * cos(alpha) 
  y <- r * sin(alpha)
  
  thousand_x <- c(thousand_x, x)
  thousand_y <- c(thousand_y, y)
}
```

Calculating the memory score based on random distribution of 1000 locations within the arena

```{r calculating memory score (random), eval=data_here}
Sum_all <- Sum_all %>% mutate(memoryScoreRand = NA, memoryScoreTraj = NA) #creating 2 new columns in the summary dataframe

for (i_trial in 1:nrow(Sum_all)) {
  farther <- 0
  for (i_point in points) {
    #for each location distance to the true location of the cued object is calculated
    distance = dist(thousand_x[i_point], thousand_y[i_point], Sum_all$objX[i_trial], Sum_all$objY[i_trial])
    
    #if the distance is bigger than the distance error then 1 is added to the count "farther"
    if (distance > Sum_all$error[i_trial]) {farther <- farther+1} else {farther <- farther}
  }
  #final score is calculating the proportion of the 1000 locations that are farther from the true location than the remembered location
  Sum_all$memoryScoreRand[i_trial] <- farther/1000
}
```

### Based on 1000 locations taken from the participant's trajectory

Calculating memory scores based on 1000 points taken from the complete trajectory of the participant

```{r calculating memory score (trajectory), eval=data_here}
#basically row counter
trials <- 0 
for (i_sub in subjects) {
  #selecting 1000 random locations from participant's overall trajectory
  XY <- filter(Traj, ID == i_sub) %>% select(ID, charX, charY)
  XY <- XY[sample(nrow(XY), 1000), ]
  for (i_trial in 1:nrow(filter(Sum_all, ID == i_sub))) {
    farther <- 0
    for (i_point in 1:length(points)) {
      #for each location distance to the true location of the cued object is calculated
      distance = dist(XY$charX[i_point], XY$charY[i_point], Sum_all$objX[i_trial+trials], Sum_all$objY[i_trial+trials])
      
      #if the distance is bigger than the distance error then 1 is added to the count "farther"
      if (distance > Sum_all$error[i_trial+trials]) {farther <- (farther+1)}
    }
    
    #final score is calculating the proportion of the 1000 locations that are farther from the true location than the remembered location
    Sum_all$memoryScoreTraj[i_trial+trials] <- farther/1000
  }
  trials <- trials + nrow(filter(Sum_all, ID == i_sub))
}
```

## Saving the compiled dataset

Last changes before saving the datasets into big files


Rearrange the columns into more cohesive order and replacing the local ID with a new ID that is necessary for data transfer.
```{r organising Sum_all better, eval=data_here}
Sum_all <- Sum_all %>%
  relocate(newID, age, age_c, block, miniblock, mini, objectTrial, trial, cue, object, 
           sec2Beg, dropTime, secTrialRepl, trialLen, sec2End, 
           landmarkX, landmarkY, landmarkZ, objX, objY, objZ, remLocX, remLocY, remLocZ, 
           error, distanceTo1, distanceTo2, distanceTo3, averageDist, memoryScoreRand, memoryScoreTraj, 
           landmarkCuePosX, landmarkCuePosY, boundaryCuePosX, boundaryCuePosY, relativeInfluence, cueDissonance, 
           trueAngle, estAngle, angleError) %>%
  select(-ID) %>%
  rename(ID = newID)
```


Replacing local ID with a new ID that is necessary for data transfer, this time in Trajectory dataframe. 

```{r, eval=data_here}
Traj <- Traj %>%
  select(-ID) %>%
  rename(ID = newID)
```


Explanations of all columns:  

- ID - randomly assigned ID of 4 digits  
- age - 8-15 years old (entered as character atm)  
- age_c - centered age
- block - 1-4  
- miniblock - 1-4 within block (in each miniblock each object appears once)  
- mini - centered miniblocks
- objectTrial - 1-16, miniblocks throughout the experiment (in objectTrial 12, participants see a object for 12th time)  
- trial - 1-16 within block  
- cue - landmark vs boundary, randomly assigned in an input files  
- cueMM - i.e. cue fro Mixed Models is a recoded version of cue to -1 and 1
- cue1 - 1-2, to get rid of object names (landmark object 1, landmark object 2, boundary object 1, boundary object 2)  - currently not generated
- object - "monster", "partyhat", "lamp", "flower"  
- sec2Beg - seconds from the beginning of the experiment to the beginning to the trial  
- dropTime - seconds from the beginning of the experiment to the indication of remembered location of the cued object  
- secTrialRepl - seconds from the beginning of the trial to the indication of remembered location of the cued object  
- trialLen - trial length in seconds  
- sec2End - seconds from the beginning of the experiment to the end of the trial  
- landmarkX - position of landmark X coordinate  
- landmarkY - position of landmark Y coordinate  
- landmarkZ - position of landmark Z coordinate (not really used/useful)  
- objX - position of the cued object of the trial X coordinate  
- objY - position of the cued object of the trial Y coordinate  
- objZ - position of the cued object of the trial Z coordinate (not really used/useful)  
- remLocX - position participant indicated as the location of the cued object X coordinate  
- remLocY - position participant indicated as the location of the cued object Y coordinate  
- remLocZ - position participant indicated as the location of the cued object Z coordinate  
- error - distance between the remembered location and the true location of the cued object  
- distanceTo1 - distance between the remembered location and a wrong/uncued object 1  
- distanceTo2 - distance between the remembered location and a wrong/uncued object 2  
- distanceTo3 - distance between the remembered location and a wrong/uncued object 3  
- averageDist - average distance between the from remembered location and the other objects  
- memoryScoreRand - memory score calculated based on randomly distributed 10,000 points  
- memoryScoreTraj - memory score calculated based on randomly picked 10,000 points from the participant's recorded path  
- landmarkCuePosX - position of the cued object based on landmark (as if landmark-dependent) X coordinate, used for relative influence score  
- landmarkCuePosY - position of the cued object based on landmark (as if landmark-dependent) Y coordinate, used for relative influence score  
- boundaryCuePosX - position of the cued object based on boundary (as if boundary-dependent) X coordinate, used for relative influence score  
- boundaryCuePosY - position of the cued object based on boundary (as if boundary-dependent) Y coordinate, used for relative influence score  
- relativeInfluence - relative influence score (distance to landmark-dependent location / (distance to landmark-dependent location + distance to boundary-dependent location))  
- cueDissonance - distance to the correct location/ (distance to the correct location + distance to location predicted by the other cue)
- trueAngle - correct angle to the cued object from the current participant's location  
- estAngle - indicated angle to the cued object from the current participant's location  
- angleError - difference between trueAngle and estAngle  
- landmarkAngle - angle to a object location predicted by landmark  
- boundaryAngle - angle to a object location predicted by boundary  
- relativeAngle - relative influence score of angle estimation (landmarkAngle/ (landmarkAngle+boundaryAngle))  
- cueDissonanceAngle - angle to the correct location/ (angle to the correct location + angle to location predicted by the other cue)
- charX - participant's position when estimating the angle X coordinate  
- charZ - participant's position when estimating the angle Z coordinate  
- charY - participant's position when estimating the angle Y coordinate  
- secTrialEst - seconds from the beginning of the trial to the angle estimation  
- sec2Est - seconds from the beginning of the experiment to the angle estimation  


Saving these into text files into our local data folder.

```{r writing big file, eval=data_here}
write.table(Sum_all, file = here("data", "Sum.txt"), sep = " ", row.names = FALSE, col.names = TRUE)  
write.table(Traj, file = here("data", "Traj.txt"), sep = " ", row.names = FALSE, col.names = TRUE) 
```


