---
title: "analysis"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
---
# Analysis

## Hypothesis

Hypothesis: Boundary-dependent object position memory will improve between 8 and 15 years of age, while landmark-dependent object memory will stay relatively constant.

## Set up
```{r}
knitr::opts_chunk$set(echo = TRUE)
```

Packages used for data analysis

```{r, warning=FALSE}
library(here)
library(tidyverse)
library(broom)
library(lme4)
library(sjPlot)
library(effsize)
library(scico)
library(cowplot)
library(gghalves)
library(ggnewscale)
library(ggeffects)
library(ggsignif)
library(patchwork)
library(Cairo)
```

Functions written for this analysis

```{r}
#function circleFun() generates locations of 100 points that are in shape of circle
#used for mapping out the arena in graphs
circleFull <- function(center = c(0,0), r = 27.5, npoints = 100){
    tt <- seq(0,2*pi,length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}

#function dist() calculates distance between given 2 points (loc1, loc2) while taking in their X and Y separately
dist <- function(loc1X, loc1Y, loc2X, loc2Y) {
   d = sqrt(((loc1X-loc2X)**2)+((loc1Y-loc2Y)**2))
   return(d)
}

```

Following chunk checks whether a folder "figures" exists and potentially creates one

```{r, eval=FALSE}
if (!dir.exists(here("figures"))){dir.create(here("figures"))}
```

Reading in the two big files containing the full dataset 

```{r data}
Sum_all <- read_delim(here("data" ,"Sum.txt"), delim = " ", 
                      col_names = TRUE, col_types = "fdddddddfdcddddddddddddddddddddddddddddddddddddddd") 
Traj <- read_delim(here("data" ,"Traj.txt"), delim = " ", 
                   col_names = TRUE, col_types = "fddddddddddddcd") 
```

Creating a list of subject IDs from the full dataset

```{r}
#generating subject ID list
subjects <- unique(Sum_all$ID)
```

Formatting for results output
```{r}
low_p <- "<0.001"
```

### Exclusion criteria

Participants are excluded based on performance in block 1 which is quantified using memory scores. 

**Explanation graph**

Graph below visualizes the calculation of memory score for a single trial. 

```{r visualization of calculation of memory scores} 
#data sorting
i_sub = subjects[5] #randomly selection one participant
XY <- filter(Traj, ID == i_sub) %>% select(ID, charX, charY) #filtering the full trajectory of the participant
XY <- XY[sample(nrow(XY), 1000), ] #selecting randomly 1000 frames from the participant's complete trajectory
graph_sub <- filter(Sum_all, ID == i_sub) #filtering the summary data of the participant
XY <- mutate(XY, distance = NA, outside = NA) #creating 2 new columsn for the trajectory data frame
for (i_point in 1:1000){ 
  #calculating the distance between the random trajectory location and the true location of the cued bject in the given trial
  dista = dist(XY$charX[i_point], XY$charY[i_point], graph_sub$objX[10], graph_sub$objY[10]) 
  XY$distance[i_point] <- dista #adding the distance value to the dataframe
  #evaluating whether the distance between the random location and the object is bigger or smaller than the distance error in the given trial
  if (dista > graph_sub$error[10]) {XY$outside[i_point] <- TRUE} else {XY$outside[i_point] <- FALSE}
}

#final used data
outside <- filter(XY, outside == TRUE) #creating separate dataframe for locations that are further from the object than the distance error
inside <- filter(XY, outside == FALSE) #creating separate dataframe for locations that are closer to the object than the distance error
littleCircle <- circleFull(center=c(graph_sub$objX[10],graph_sub$objY[10] ), r=graph_sub$error[10]) #circle dividing closer/further locations
circle <- circleFull() #arena border visualization 

#graph
mem_score <- ggplot(circle, aes(x, y)) +
  geom_path() +
  geom_path(subset(Traj, ID %in% i_sub), mapping=aes(x=charX, y=charY), size=0.2, alpha=0.7, linetype = 1) +
  geom_point(data= outside, aes(x=charX, y=charY, color="Trajectory Locations Further"), size=0.7, alpha=0.7) +
  geom_point(data=inside, aes(x=charX, y=charY, color="Trajectory Locations Closer"), size=0.7) +
  geom_path(data=littleCircle, aes(x,y), color="#E58A50") +
  geom_point(data=graph_sub, aes(x=objX[10], y=objY[10], color="True Object Location"), size = 2) +
  geom_point(data=graph_sub, aes(x=remLocX[10], y=remLocY[10], color="Remembered Object Location"), size=2) +
  theme_cowplot() +
  theme(aspect.ratio=1, 
        axis.title = element_text(size=10), axis.text = element_text(size=10), 
        plot.title = element_text(size=12), plot.subtitle = element_text(size = 11)) +
  labs(title = "Memory score calculation based on trajectory", 
       subtitle = paste("Number of Trajectory Locations Closer / 1000" ,
                        paste("Memory score:", graph_sub$memoryScoreTraj[10]), sep="\n"), 
       x= 'X (virtual meters)', 
       y= 'Y (virtual meters)') +
  scale_color_manual(name = " ", 
                     values= c("True Object Location" = "#F8DF77", "Remembered Object Location" = "#95413F", 
                               "Trajectory Locations Closer" = "#E58750", "Trajectory Locations Further" = "#191900"))

ggsave(filename="memory_score_visual.pdf", plot=mem_score, units = "cm", width = 15, height = 11, dpi = "retina", 
       device = cairo_pdf, path = here("figures"))
ggsave("memory_score_visual.png", plot=mem_score, units = "cm", width = 15, height = 11, 
       dpi = "retina", device = "png", path = here("figures"))

mem_score
```

To be included in the analysis, participant's memory scores from block 1 need to be significantly greater than the chance level 0.5.
```{r exclusion t-test}
exclusion <- c() #creating empty list that will contain the subject IDs that will be excluded
for (i_sub in subjects) {
  score <- t.test(subset(Sum_all, ID==i_sub & block==1)$memoryScoreTraj, 
                  mu=0.5, alternative = "greater") %>% tidy() #one-tailed t.test of block 1 memory scores against chance level 0.5
  if (score$p.value > 0.05) {
    exclusion <- c(exclusion, i_sub)
    Sum_all <- filter(Sum_all, ID != i_sub)
    }
}
```

- number of participants excluded: `r length(exclusion)`
- new overall sample size: `r length(subjects)-length(exclusion)`


### Timeout sessions

Identifying and filtering timeout sessions which are encoded as distance error = -1 (an impossible value)

```{r}
#summary of timeout trials 
timeout <- filter(Sum_all, error == -1)

#filtering timeout trials as they do not include location estimation
Sum_all <- filter(Sum_all, error != -1)
```

- number of timeout trials: `r nrow(timeout)`
- number of participants with timeout trials: `r length(unique(timeout$ID))`
- average number of timeout trials per participant with timeout trials: `r round(nrow(timeout)/length(unique(timeout$ID)), 3)` (sd = )
- average number of timeout trials per participant: `r round(nrow(timeout)/length(subjects), 3)` (sd = )


## Incomplete datasets
````{r}
incomplete <- Sum_all %>%
  group_by(ID) %>%
  summarise(n = n())

complete <- length(subset(incomplete, n == 64)$n)
incomplete <- length(subset(incomplete, n < 64)$n)
```

- complete datasets: `r complete` 
- incomplete datasets: `r incomplete` 


## Descriptives

**Age Distribution**

Graph below shows the age distribution of our participants.

```{r}
#summarising data to get a single line for each participant
age <- Sum_all %>%
  group_by(ID, age) %>%
  summarise(n = n(), .groups="drop")

age_mean <- summarise(age, mean = mean(age), sd=sd(age))

age_graph <- ggplot(age, aes(x=age)) + 
  geom_bar(fill=scico(1, palette="acton", begin=0.8)) +
  theme_cowplot() +
  background_grid(major="y", minor="y") +
  scale_x_continuous(breaks = c(8,9,10,11,12,13,14,15)) +
  theme(legend.position = "none", plot.title = element_text(size=12), axis.title = element_text(size=10)) +
  labs(x="Age", y="Count", title="Distribution of age") 

#saving the graph as pdf and png 
ggsave("age.pdf", plot=age_graph, units = "cm", width = 8, height = 6, dpi = "retina", 
       device = cairo_pdf, path = here("figures"))
ggsave("age.png", plot=age_graph, units = "cm", width = 8, height = 6, dpi = "retina", 
       device = "png", path = here("figures"))

age_graph
```

- mean age: `r age_mean$mean`
- sd age: `r age_mean$sd`


**Reaction Time**

Next, we looked into reaction time (seconds between angle estimation and location estimation). 

```{r}
#average RT 
reaction_time_dat <- Sum_all %>%
  mutate(posResponse = secTrialRepl - secTrialEst) %>% #calculating the seconds between angle estimation and location estimation
  group_by(ID, age) %>%
  summarise(posiMemResponse = mean(posResponse), .groups="drop") 

#raincloud graph showing distribution of RT, 1 point per participant
ggplot(reaction_time_dat, aes(x=0, y=posiMemResponse)) +
  geom_half_violin(aes(x=-0.05), fill=scico(1, palette = "acton", begin = 0.45), alpha =0.5, color=NA) +
  geom_point(aes(x=0.105, color=age), position = position_jitter(width =0.05, height = 0), shape=16, size = 2) +
  scale_color_scico(palette = "acton") +
  geom_boxplot(width = .08, outlier.shape = NA) +
  theme_cowplot() +
  ylab('RT') + xlab('') + ggtitle('Average reaction time for each participant across the entire experiment') +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        aspect.ratio =1, 
        plot.title = element_text(face="italic", size=12))

#average RT and sd for the full dataset
reaction_time <- summarise(reaction_time_dat, 
                           mean = mean(posiMemResponse), sd=sd(posiMemResponse), min=min(posiMemResponse), max=max(posiMemResponse)) 

reaction_time

```

The average reaction time was `r round(reaction_time$mean, 3)` seconds (sd = `r round(reaction_time$sd, 3)`).

**Trial Length**

We also calculated the average length of a single trial.

```{r}
#average trial length for the full dataset
trial_length <- Sum_all %>% 
  summarise(mean = mean(trialLen), sd = sd(trialLen), min = min(trialLen), max = max(trialLen))

```

The average trial length was `r round(trial_length$mean, 3)` seconds (sd = `r round(trial_length$sd, 3)`).

```{r, include=FALSE}
i_sub = subjects[5]
graph_sub <- filter(Sum_all, ID == i_sub & objectTrial == 1)
locations <- ggplot(data=circleFull(), aes(x, y)) +
  geom_path() +
  geom_path(data=circleFull(center=c(graph_sub$landmarkX[1],graph_sub$landmarkY[1] ), r=8),color="red") + 
  geom_path(data=circleFull(center=c(graph_sub$landmarkX[1],graph_sub$landmarkY[1] ), r=13),color="red") + 
  geom_point(data=graph_sub, aes(x=landmarkX[1], y=landmarkY[1]), shape=4, color="red", size=3) +
  geom_path(data=circleFull(r=14.5), color="blue") + 
  geom_path(data=circleFull(r=19.5), color="blue") + 
  geom_point(data=graph_sub, aes(x=objX, y=objY, color=cue)) +
  scale_color_manual(values = c("red", "blue"), labels=c("Landmark", "Boundary")) + 
  theme_cowplot() + 
  theme(#spect.ratio = 1,
        axis.title = element_blank(),
        axis.text = element_text(size=10),
        plot.margin = margin(l = 0.5, unit="cm")) +
  labs(title="Restrictions of locations of the objects", color="Cue")

ggsave("location_restrictions.png", plot=locations, units = "cm", width = 10, height = 9, 
       dpi = "retina", device = "png", path = here("figures"))

locations
```

```{r, include=FALSE}
i_sub = subjects[5]
graph_sub <- filter(Sum_all, ID == i_sub & miniblock==1)
blocks <- ggplot(data=circleFull(), aes(x, y)) +
  geom_path() +
  geom_path(data=circleFull(center=c(60,0))) + 
  geom_path(data=circleFull(center=c(120,0))) + 
  geom_path(data=circleFull(center=c(180,0))) + 
  geom_point(data=graph_sub, aes(x=landmarkX[5]+60, y=landmarkY[5]), shape=4, color="red", size=2) +
  geom_point(data=graph_sub, aes(x=landmarkX[9]+120, y=landmarkY[9]), shape=4, color="red", size=2) +
  geom_point(data=graph_sub, aes(x=landmarkX[13]+180, y=landmarkY[13]), shape=4, color="red", size=2) +
  geom_point(data=graph_sub, aes(x=landmarkX[1], y=landmarkY[1]), shape=4, color="red", size=2) +
  geom_point(data=graph_sub %>% filter(block==1), aes(x=objX, y=objY, color=cue)) +
  geom_point(data=graph_sub %>% filter(block==2), aes(x=objX+60, y=objY, color=cue)) +
  geom_point(data=graph_sub %>% filter(block==3), aes(x=objX+120, y=objY, color=cue)) +
  geom_point(data=graph_sub %>% filter(block==4), aes(x=objX+180, y=objY, color=cue)) +
  scale_color_manual(values = c("red", "blue"), labels=c("Landmark", "Boundary")) + 
  theme_blank() + 
  theme(#aspect.ratio = 0.23,
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(),
        title = element_text(size=10, face="bold"),
        legend.position = "none") +
  labs(title="Locations of the objects throughout the experiment", color="Cue") +
  scale_x_continuous(breaks = c(0, 60, 120, 180), labels = c("Block 1", "Block 2", "Block 3", "Block 4"))

ggsave("location_blocks.png", plot=blocks, units = "cm", width = 15.9, height = 6, 
       dpi = "retina", device = "png", path = here("figures"))

blocks
```

```{r. include=FALSE}
layout <- "
AAAA####
AAAA####
AAAA####
AAAA####
AAAA####
BBBBBBBB
BBBBBBBB
BBBBBBBB
"

locs <- locations + blocks +
  plot_layout(design=layout) &
  theme(plot.title = element_text(size=12, face = "italic"),
        axis.text = element_text(size=10),
        legend.title = element_text(size=12),
        plot.tag = element_text(vjust=1)) &
  plot_annotation(tag_levels = 'A')

ggsave("locations.png", plot=locs, units = "cm", width = 15.9, height = 12.4, 
       dpi = "retina", device = "png", path = here("figures") )

locs
```

## Block 1 Performance

This subsection of the analysis aims to answer whether the participants completed the basic task according to the instructions before any manipulation was introduced.

### Recalled locations 
First, we wanted to visualize the recalled locations relative to the object location so we calculated a new "error location" as if the cued object was at coordinate 0,0 inside the arena and created a heat map. The boundary of the arena is drawn in white.
```{r heat map}
#creating a smaller data frame for trials only in block 1 and calculating the new error coordinates (newX, newY)
heatMapDat <- Sum_all %>%
  filter(block==1) %>% 
  select(ID, miniblock, objX, objY, remLocX, remLocY, cue, block) %>% 
  mutate(newX = remLocX-objX, newY = remLocY - objY) 

#graphing
heat_map_B1 <- ggplot(heatMapDat, aes(x=newX, y=newY)) + 
  # creating a heat map
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE, na.rm=TRUE) +
  # setting a color palette from scico package
  scale_fill_scico(palette = 'lajolla', begin=1, end=0, name = "Density") +
  # adding individual error locations on top in white
  geom_point(alpha=0.2, color="white", size=0.05) +
  # adding the boundary of the arena (as a reference for distance)
  geom_path(data = circle, aes(x, y), color="grey") +
  # plotting the x and y axis on 0,0 to visualize the center of the arena
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0) +
  #changing titles 
  labs(x = "Error on X (vm)", y = "Error on Y (vm)", title="Centralised Distribution of Error") +
  # aesthetical changes
  theme_cowplot() +
  theme(aspect.ratio=1,
        plot.title = element_text(face="italic", size=12),
        legend.title = element_text(size=10),
        legend.text = element_text(size=10)) +
  # adjusting axis limits and breaks
  scale_x_continuous(limits = c(-33, 33), breaks = c(-30, -20, -10, 0, 10, 20, 30)) + 
  scale_y_continuous(limits = c(-33, 33), breaks = c(-30, -20, -10, 0, 10, 20, 30)) 

#saving the graph as pdf and png 
ggsave("heatMap_block1.pdf", plot=heat_map_B1, units = "cm", width = 10, height = 10, dpi = "retina", 
       device = cairo_pdf, path = here("figures"))
ggsave("heatMap_block1.png", plot=heat_map_B1, units = "cm", width = 10, height = 10, dpi = "retina", 
       device = "png", path = here("figures"))

#show the graph
heat_map_B1
```

### Memory score

```{r summarise data for block 1}
#creating dataset that only contains data from block 1 and summarizing for each participant
summaryBlock1 <- Sum_all %>% 
  filter(block==1) %>% 
  group_by(ID, block) %>% 
  summarise(memoryScore = mean(memoryScoreTraj), distanceOther = mean(averageDist), distanceTrue = mean(error), .groups="drop")
```

To tested whether the memory scores are above chance level 0.5, we ran one sample, one tail t-test.

```{r memory score vs 0.5, one-sample t-test}
b1_stats <- t.test(summaryBlock1$memoryScore, mu = 0.5, alternative="greater") %>% tidy()

d <- cohen.d(d=summaryBlock1$memoryScore, f=NA, mu=0.5) 

b1_stats$d <- d$estimate
b1_stats$dCI_low <- d$conf.int[[1]]
b1_stats$dCI_high <- d$conf.int[[2]]
```

*Block 1 memory score t-test results:*

t(`r b1_stats$parameter`)= `r round(b1_stats$statistic, 2)`, p`r if (b1_stats$p.value > 0.001) {paste("=", round(b1_stats$p.value, 3))} else {low_p}`, d=`r round(b1_stats$d, 2)`, 
95% CI [`r round(b1_stats$dCI_low, 2)`, `r round(b1_stats$dCI_high, 2)`]



Raincloud graph below visualizes the distribution of average memory scores in block 1 (1 point per participant)

```{r memory score graph}
mem_score_B1 <- ggplot(summaryBlock1, aes(x=block, y= memoryScore)) + 
  # violin plot
  geom_half_violin(aes(x=block-0.06), fill=scico(1, palette = "lajolla", begin = 0.45), alpha =0.5, color=NA) +
  # single subject data points (1 per participant) with horizontal jitter
  geom_point(aes(x=block+0.08), position = position_jitter(width =0.01, height = 0), shape=16, size = 1) +
  # boxplot of distribution (median, 1st and 3rd quartile)
  geom_boxplot(width = .05, outlier.shape = NA) +
  # adding plot of mean and SEM  
  stat_summary(fun = mean, geom = "point", size=1, shape = 16,
               position = position_nudge(-.06), colour = "black") + 
  stat_summary(fun.data = mean_se, geom = "errorbar",
               position = position_nudge(-.06), colour = "black", width = 0, size = 0.5) +
  # adding horizontal line at chance level 0.5 with annotation
  geom_hline(yintercept = 0.5, linetype=2) +
  annotate("text", label="chance = 0.5", x=1.2, y=0.52, size=3) +
  # correcting labels
  labs(x = '', y = 'Memory Score (0-1)', title = 'Memory score') +
  # aesthetical changes
  theme_cowplot() +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        aspect.ratio = 1, 
        plot.title = element_text(face="italic", size=12)) 

#saving the graph as pdf and png
ggsave("memory_score_B1.pdf", plot=mem_score_B1, units = "cm", width = 10, height = 7, 
       dpi = "retina", device = cairo_pdf, path = here("figures"))
ggsave("memory_score_B1.png", plot=mem_score_B1, units = "cm", width = 10, height = 7, 
       dpi = "retina", device = "png", path = here("figures"))

#show the graph 
mem_score_B1
```

Assembly of graphs for positional memory in block 1.

```{r, eval=FALSE}
# using patchwork package to combine 2 separate graphs 
memory_B1 <- mem_score_B1 + heat_map_B1 &
  theme(axis.text = element_text(size=10), 
        axis.title = element_text(size=10), 
        plot.title = element_text(size=12)) &
  plot_annotation(title = 'Memory Performance in Block 1',
                  theme = theme(plot.title = element_text(size = 12, face="bold"))) 

# saving the compiled graphs as pdf and png
ggsave("Block1_loc.pdf", plot=memory_B1, 
       units = "cm", width = 15.9, height = 10, dpi = "retina", device = cairo_pdf, path = here("figures"))
ggsave("Block1_loc.png", plot=memory_B1, 
       units = "cm", width = 15.9, height = 10, dpi = "retina", device = "png", path = here("figures"))

# show the compiled graphs
memory_B1
```

### Distance from remembered locations to other locations

We wanted to check that participants tried to recall the location of the correct object and did not mistake it with other 3 objects on regular basis so we calculated the average distance from the recalled location to the other objects' locations (distanceToOther1 + distanceToOther2 + distanceToOther3 / 3) and compared it to the distance error to the true location of the cued object. This calculation is visualized in a graph below for a single example trial. 

```{r}
#filtering for only trials in 1 miniblock for simplicity
graph_sub <- graph_sub %>% 
  filter(objectTrial == 5)

distance_other <- ggplot(circle, aes(x, y)) +
  # creating arena boundary
  geom_path() +
  # true location of cued object 
  geom_point(data=graph_sub, aes(x=objX[2], y=objY[2], color="True Object Location"), size = 2.5) +
  # line visualizing the distance error (between recalled location and true location)
  geom_segment(data=graph_sub, aes(x=remLocX[2], y=remLocY[2], xend= objX[2], yend= objY[2], color="True Object Location"), alpha=.5) +
  # location of other object 1 & distance to the recalled location
  geom_point(data=graph_sub, aes(x=remLocX[1], y=remLocY[1], color="Other Object Location"), size=2.5) +
  geom_segment(data=graph_sub, aes(x=remLocX[1], y=remLocY[1], xend= remLocX[2], yend= remLocY[2], color="Other Object Location"), alpha=.5) +
  # location of other object 2 & distance to the recalled location
  geom_point(data=graph_sub, aes(x=remLocX[3], y=remLocY[3], color="Other Object Location"), size=2.5) +
  geom_segment(data=graph_sub, aes(x=remLocX[3], y=remLocY[3], xend= remLocX[2], yend= remLocY[2], color="Other Object Location"), alpha=.5) +
  # location of other object 3 & distance to the recalled location
  geom_point(data=graph_sub, aes(x=remLocX[4], y=remLocY[4], color="Other Object Location"), size=2.5) +
  geom_segment(data=graph_sub, aes(x=remLocX[4], y=remLocY[4], xend= remLocX[2], yend= remLocY[2], color="Other Object Location"), alpha=.5) +
  # recalled location of the cued object
  geom_point(data=graph_sub, aes(x=remLocX[2], y=remLocY[2], color="Remembered Object Location"), size=2.5) +
  # aesthetical changes
  theme_cowplot() +
  theme(aspect.ratio=1, 
        axis.title = element_text(size=10), axis.text = element_text(size=10), 
        plot.title = element_text(size=12), plot.subtitle = element_text(size = 11)) +
  # changing labels and title
  labs(title = "Distance from remembered location to other locations", 
       subtitle = paste(sprintf("Distance Error: %s vm", graph_sub$error[2]), 
                        sprintf("Average Distance to Other Objects: %s vm", round(graph_sub$averageDist[2], 2)), sep="\n"),  
       x= 'X (vm)',  y= 'Y (vm)') +
  # specifying colors manually 
  scale_color_manual(name = " ", 
                     values= c("True Object Location" = "#883E3A", "Remembered Object Location" = "#E37D50", 
                               "Other Object Location" = "#F6D868"))

# saving graph as pdf and png
ggsave(filename="distance_other_visual.pdf", plot=distance_other, units = "cm", width = 15, height = 11, dpi = "retina", 
       device = cairo_pdf, path = here("figures"))
ggsave("distance_other_visual.png", plot=distance_other, units = "cm", width = 15, height = 11, 
       dpi = "retina", device = "png", path = here("figures"))

# show the graph
distance_other
```

To test this, we ran paired t-test which showed that on average there is a difference between these 2 distances.

```{r distance to incorrect objects vs the cued object t-test}
dist_stats <- t.test(summaryBlock1$distanceTrue, summaryBlock1$distanceOther, paired = TRUE) %>% tidy()

d <- cohen.d(summaryBlock1$distanceTrue, summaryBlock1$distanceOther, paired = TRUE) 

dist_stats$d <- d$estimate
dist_stats$dCI_low <- d$conf.int[[1]]
dist_stats$dCI_high <- d$conf.int[[2]]
```

*Block 1 distance error t-test results:*

t(`r dist_stats$parameter`)= `r round(dist_stats$statistic, 2)`, p`r if (dist_stats$p.value > 0.001) {paste("=", round(dist_stats$p.value, 3))} else {low_p}`, d=`r round(dist_stats$d, 2)`, 95% CI [`r round(dist_stats$dCI_low, 2)`, `r round(dist_stats$dCI_high, 2)`]


Graph visualizing this comparison is below.

```{r pivoting the summary for the graph}
#necessary pivoting of the dataset for the following graph
summaryBlock1 <- pivot_longer(summaryBlock1, cols=c(distanceTrue, distanceOther))
```

```{r distance error visualization}
distance_B1 <- ggplot(summaryBlock1, aes(x=name, y= value)) + 
  # specifying axis limits and breaks
  scale_x_discrete(limits = c('distanceTrue', 'distanceOther'),
                   labels = c('to Correct Location', 'to Other Object Locations')) + 
  scale_y_continuous(limits = c(0, 28), breaks = c(5, 10, 15, 20 , 25)) +
  # violin plot 
  gghalves::geom_half_violin(data=summaryBlock1 %>% filter(name=="distanceOther"), 
                             position=position_nudge(+0.2), aes(fill=name),alpha =0.7, color=NA, side="r") +
  gghalves::geom_half_violin(data=summaryBlock1 %>% filter(name=="distanceTrue"), 
                             position=position_nudge(-0.2), aes(fill=name),alpha =0.7, color=NA, side="l") + 
  # scico palette lajolla for violin plot fill
  scale_fill_scico_d(palette = 'lajolla', begin=0.2, end=0.75) +
  # single subject data points (1 per participant)
  geom_point(shape=16, size = 1) +
  # boxplot of distribution (median, 1st and 3rd quartile)
  geom_boxplot(data=summaryBlock1 %>% filter(name=="distanceOther"), 
               position=position_nudge(+0.1), width = .1, outlier.shape = NA) +
  geom_boxplot(data=summaryBlock1 %>% filter(name=="distanceTrue"), 
               position=position_nudge(-0.1), width = .1, outlier.shape = NA) +
  # adding plot of mean and SEM  
  stat_summary(data=summaryBlock1 %>% filter(name=="distanceOther"), 
               position=position_nudge(+0.2), fun = mean, geom = "point", size=1, shape = 16, colour = "black") + 
  stat_summary(data=summaryBlock1 %>% filter(name=="distanceOther"), 
               position=position_nudge(+0.2), fun.data = mean_se, geom = "errorbar", colour = "black", width = 0, size = 0.5) +
  stat_summary(data=summaryBlock1 %>% filter(name=="distanceTrue"), 
               position=position_nudge(-0.2), fun = mean, geom = "point", size=1, shape = 16, colour = "black") + 
  stat_summary(data=summaryBlock1 %>% filter(name=="distanceTrue"), 
               position=position_nudge(-0.2), fun.data = mean_se, geom = "errorbar", colour = "black", width = 0, size = 0.5) +
  # line connecting individual participants' values 
  geom_line(aes(group=ID), alpha=0.5) +
  # changing title and labels
  labs(x = " ", y = "Distance (vm)", subtitle = "In Block 1", 
       title = "Distance from Remembered Location to Object Locations") + 
  # aesthetical changes
  theme_cowplot() +
  theme(legend.position = "none", 
        plot.title = element_text(size=12, lineheight = 1.1), 
        plot.subtitle = element_text(face = "bold", lineheight = 1.1),
        aspect.ratio = 0.55,
        axis.title = element_text(size=12)) +
  # visualizing the significance of the t-test
  geom_signif(comparisons = list(c("distanceTrue", "distanceOther")), test="t.test", 
              test.args=list(alternative = "two.sided", var.equal = FALSE, paired=TRUE),
              map_signif_level = TRUE, tip_length = 0, extend_line = 0.045, y_position = 26)

# saving the graph as pdf and png
ggsave("distances_B1.pdf", plot=distance_B1, 
       units = "cm", width = 13, height = 10, dpi = "retina", device = cairo_pdf, path = here("figures"))
ggsave("distances_B1.png", plot=distance_B1, 
       units = "cm", width = 13, height = 10, dpi = "retina", device = "png", path = here("figures"))

# show the graph
distance_B1
```

## Cue Differences

Next we wanted to investigate whether the participants followed the cues in block 2-4 after landmark and landmark-dependent object movement. 
Also, is there performance difference between landmark- vs boundary-dependent objects?

### Relative Influence

Relative Influence has been used in the field for over a decade now, initially introduced in paper by Doeller, King and Burgess (2008). 

>"For blocks 2–4, we attempted to quantify the relative influence of either cue on each response location. In a pilot study, we noticed that incorrect responses tended to be clustered around locations previously associated with the incorrect cue: either during block 1 or during the immediately preceding block. Accordingly, we calculated the relative influence of boundary versus landmark in blocks 2–4 as d L/(d L + d B), where d L is the distance of the response from the location predicted by the landmark and d B is the distance from the location predicted by the boundary. This measure varies between 0 (using the landmark) and 1 (using the boundary). On the basis of our pilot data the incorrect cue potentially predicts two different locations in blocks 3 and 4 (reflecting the object's positions relative to it in the preceding block and in block 1): we used whichever was closest to the response location."

**Explanation Graph** 

Below, the calculation of relative influence score is visualised. 

```{r}
#loading a data from block 2-4 for a single participant
graph_sub <- filter(Sum_all, ID == subjects[5] & block == 4 & trial==15) 


relativeInf_graph <- ggplot(data=graph_sub) +
  # location predicted by landmark
  geom_point(aes(x=landmarkCuePosX, y=landmarkCuePosY, color="Location Predicted by Landmark"), size = 2.5) +
  # line visualizing the distance error (between recalled location and landmark-predicted location)
  geom_segment(aes(x=remLocX, y=remLocY, xend= landmarkCuePosX, yend=landmarkCuePosY, 
                                   color="Location Predicted by Landmark"), size=0.8) +
  # adding dL label
  annotate("text", label="dL", x=-7.9, y=-8.5, size=4, color="#C6F1B1", fontface =2) +
  # location predicted by boundary
  geom_point(aes(x=boundaryCuePosX, y=boundaryCuePosY, color="Location Predicted by Boundary"), size = 2.5) +
  # line visualizing the distance error (between recalled location and true location)
  geom_segment(aes(x=boundaryCuePosX, y=boundaryCuePosY, xend= remLocX, yend= remLocY,
                                   color="Location Predicted by Boundary"), alpha=.7 , size=0.8) +
  # adding dB label
  annotate("text", label="dB", x=10.5, y=3, size=4, color="#592758", fontface =2) +
  #recalled location
  geom_point(aes(x=remLocX, y=remLocY, color = "Remembered Object Location"), size = 2.5) +
  #landmark location 
  geom_point(aes(x=landmarkX, y=landmarkY), shape = 15, color = "#94A98F", size=3) +
  annotate("text", label="Landmark", x= -16, y = -3.5, size=3.5, color= "#94A98F") +
  
  # creating arena boundary
  geom_path(data=circleFull(), aes(x, y)) +
  # aesthetical changes
  theme_cowplot() +
  theme(aspect.ratio=1, 
        axis.title = element_text(size=10), axis.text = element_text(size=10), 
        plot.title = element_text(size=12), plot.subtitle = element_text(size = 11)) +
  # changing labels and title
  labs(title = "Relative Influence Calculation", 
       subtitle = paste("dL / (dL + dB) ", 
                        sprintf("Relative Influence: %s ", round(graph_sub$relativeInfluence, 2)), sep="\n"),  
       x= 'X (vm)',  y= 'Y (vm)') +
  # specifying colors manually 
  scale_color_manual(name = " ", 
                     values= c("Location Predicted by Boundary" = "#592758", "Location Predicted by Landmark" = "#C6F1B1", 
                               "Remembered Object Location" = "red"))

# saving graph as pdf and png
ggsave(filename="relative_influence_visual.pdf", plot=relativeInf_graph, 
       units = "cm", width = 15, height = 11, dpi = "retina", 
       device = cairo_pdf, path = here("figures"))
ggsave("relative_influence_visual.png", plot=relativeInf_graph, 
       units = "cm", width = 15, height = 11, 
       dpi = "retina", device = "png", path = here("figures"))

# show the graph
relativeInf_graph
```

First, let's create a subset dataframe that has data only from block 2-4 and get rid of us currently unnecessary columns. Then we summarize relative influence score, correct cue influence and distance error.

```{r summarise the data for rest of the analysis}
subset_RI <- Sum_all %>% 
  filter(block!=1) %>% 
  select(-object, -sec2Beg, -sec2Est, -dropTime, -sec2End, -trialLen, -secTrialEst) 

relativeInfluenceBlocks <- subset_RI %>%
  group_by(ID, cue) %>% 
  summarise(relativeInf = mean(relativeInfluence), 
            cueDis = mean(cueDissonance),
            distanceError = mean(error), 
            age=unique(age), 
            .groups="drop") 
```

**T-Tests**

As score 0.5 points towards location between the location predicted by landmark and location predicted by boundary, we ran a one sample, one tail t-test to test whether the relative scores for landmark-dependent objects are less than 0.5.

```{r t-test of RI vs 0.5 landmark}
landmarkRI_stats <- t.test(subset(relativeInfluenceBlocks, cue=="landmark")$relativeInf, 
       mu = 0.5, alternative = "less") %>% tidy()

d <- cohen.d(d=subset(relativeInfluenceBlocks, cue=="landmark")$relativeInf, f=NA, mu=0.5) 

landmarkRI_stats$d <- d$estimate
landmarkRI_stats$dCI_low <- d$conf.int[[1]]
landmarkRI_stats$dCI_high <- d$conf.int[[2]]
```

*Landmark-dependent objects' RI against 0.5 t-test results:*

t(`r landmarkRI_stats$parameter`)= `r round(landmarkRI_stats$statistic, 2)`, p`r if (landmarkRI_stats$p.value > 0.001) {paste("=", round(landmarkRI_stats$p.value, 3))} else {low_p}`, d=`r round(landmarkRI_stats$d, 2)`, 95% CI [`r round(landmarkRI_stats$dCI_low, 2)`, `r round(landmarkRI_stats$dCI_high, 2)`]


After we ran a one sample, one tail t-test to test whether the relative scores for boundary-dependent objects are higher than 0.5.

```{r t-test of RI vs 0.5 boundary}
boundaryRI_stats <- t.test(subset(relativeInfluenceBlocks, cue=="boundary")$relativeInf, 
       mu = 0.5, alternative = "greater") %>% tidy()

d <- cohen.d(d=subset(relativeInfluenceBlocks, cue=="boundary")$relativeInf, f=NA, mu=0.5) 

boundaryRI_stats$d <- d$estimate
boundaryRI_stats$dCI_low <- d$conf.int[[1]]
boundaryRI_stats$dCI_high <- d$conf.int[[2]]
```

*Boundary-dependent objects' RI against 0.5 t-test results:*

t(`r boundaryRI_stats$parameter`)= `r round(boundaryRI_stats$statistic, 2)`, p`r if (boundaryRI_stats$p.value > 0.001) {paste("=", round(boundaryRI_stats$p.value, 3))} else {low_p}`, d=`r round(boundaryRI_stats$d, 2)`, 95% CI [`r round(boundaryRI_stats$dCI_low, 2)`, `r round(boundaryRI_stats$dCI_high, 2)`]


We also tested these two groups against each other to see if the scores are significantly different. 

```{r t-test RI boundary vs landmark}
RI_stats <- t.test(subset(relativeInfluenceBlocks, cue=="boundary")$relativeInf, 
       subset(relativeInfluenceBlocks, cue=="landmark")$relativeInf, paired=TRUE) %>% tidy()

d <- cohen.d(subset(relativeInfluenceBlocks, cue=="boundary")$relativeInf, 
       subset(relativeInfluenceBlocks, cue=="landmark")$relativeInf, paired=TRUE) 

RI_stats$d <- d$estimate
RI_stats$dCI_low <- d$conf.int[[1]]
RI_stats$dCI_high <- d$conf.int[[2]]
```

*Boundary-dependent objects' RI vs landmark-dependent objects' RI t-test results:*

t(`r RI_stats$parameter`)= `r round(RI_stats$statistic, 2)`, p`r if (RI_stats$p.value > 0.001) {paste("=", round(RI_stats$p.value, 3))} else {low_p}`, d=`r round(RI_stats$d, 2)`, 95% CI [`r round(RI_stats$dCI_low, 2)`, `r round(RI_stats$dCI_high, 2)`]


**Graph**

This difference in relative influence scores between boundary-dependent objects and landmark-dependent objects is visualized in a graph below. 

```{r relative influence block 2-4 graph}
rel_Inf <- ggplot(relativeInfluenceBlocks, aes(x=cue, y=relativeInf)) + 
  # changing labels and titles
  scale_x_discrete(labels = c('Boundary', 'Landmark')) +
  labs(x = " ", y = "Relative Influence (0-1)", 
       title = "Positional Memory") + 
  # violin plots
  gghalves::geom_half_violin(data=relativeInfluenceBlocks %>% filter(cue=="landmark"), 
                             position=position_nudge(+0.2), aes(fill=cue),alpha =0.7, color=NA, side="r") +
  gghalves::geom_half_violin(data=relativeInfluenceBlocks %>% filter(cue=="boundary"), 
                             position=position_nudge(-0.2), aes(fill=cue),alpha =0.7, color=NA, side="l") + 
  # scico palette tokyo
  scale_fill_scico_d(palette = 'tokyo', begin=0.15, end=0.85) +
  # single subject data points (1 per participant)
  geom_point(shape=16, size = 1) +
  # line connecting individual participants' values 
  geom_line(aes(group=ID), alpha=0.5) +
  # boxplot of distribution (median, 1st and 3rd quartile)
  geom_boxplot(data=relativeInfluenceBlocks %>% filter(cue=="landmark"), 
               position=position_nudge(+0.1), width = .1, outlier.shape = NA) +
  geom_boxplot(data= relativeInfluenceBlocks %>% filter(cue=="boundary"), 
               position=position_nudge(-0.1), width = .1, outlier.shape = NA) +
  # adding plot of mean and SEM  
  stat_summary(data=relativeInfluenceBlocks %>% filter(cue=="landmark"), 
               position=position_nudge(+0.2), fun = mean, geom = "point", size=1, shape = 16, colour = "black") + 
  stat_summary(data=relativeInfluenceBlocks %>% filter(cue=="landmark"), 
               position=position_nudge(+0.2), fun.data = mean_se, geom = "errorbar", colour = "black", width = 0, size = 0.5) +
  stat_summary(data=relativeInfluenceBlocks %>% filter(cue=="boundary"), 
               position=position_nudge(-0.2), fun = mean, geom = "point", size=1, shape = 16, colour = "black") + 
  stat_summary(data=relativeInfluenceBlocks %>% filter(cue=="boundary"), 
               position=position_nudge(-0.2), fun.data = mean_se, geom = "errorbar", colour = "black", width = 0, size = 0.5) +
  # aesthetical changes
  theme_cowplot() +
  theme(legend.position = "none", 
        plot.title = element_text(size=12, lineheight = 1.1), 
        axis.title = element_text(size=10)) +
  # visualizing the significance level of the t-test
  geom_signif(comparisons = list(c("landmark", "boundary")), test="t.test", 
              test.args=list(alternative = "two.sided", paired=TRUE), 
              map_signif_level = TRUE, tip_length = 0, extend_line = 0.045, y_position = 0.83) +
  # adding line at 0.5 (not-following either cue)
  geom_hline(yintercept=0.5, linetype=2, alpha=0.6) +
  # changing limits and breaks of y-axis
  scale_y_continuous(limits=c(0.1, 0.9), breaks = c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9)) +
  # adding annotation of significance level of individual t-tests
  annotate("text", label="***", size=3, y=0.8, x=0.9, fontface =2) +
  annotate("text", label="***", size=3, y=0.15, x=2.1, fontface =2) 

# saving graphs as  pdf and png
ggsave("relativeInfluence.pdf", plot=rel_Inf, 
       units = "cm", width = 15, height = 11, dpi = "retina", device = cairo_pdf, path = here("figures"))
ggsave("relativeInfluence.png", plot=rel_Inf, 
       units = "cm", width = 15, height = 11, dpi = "retina", device = "png", path = here("figures"))

# show the graph
rel_Inf
```

**Mixed Models**

As a first step towards building a full mixed effects model, we tested a simpliest version with only cue as a fixed effect and a random slope and random intercepts for participants. We did not use cue as a factor but in a recoded version of landmark = -1 and boundary = 1.

```{r}
formulaCue <- "relativeInfluence ~ cueMM + (1+cueMM|ID)"
modelCue <- lme4::lmer(formula = formulaCue, data=subset_RI)

tab_model(modelCue, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Cue"),  
          dv.labels = "Relative Influence", 
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 
```

To test, whether cue is a significant predictor we ran a likelihood ratio test comparing our simpliest model and a model containing only random effects.

```{r}
formulaCueControl<- "relativeInfluence ~ 1 + (1+cueMM|ID)"
modelCueControl <- lme4::lmer(formula = formulaCueControl, data=subset_RI)

ratioCue <- anova(modelCue, modelCueControl) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioCue$statistic[2], 3)`, p`r if (ratioCue$p.value[2] > 0.001) {paste("=", round(ratioCue$p.value[2], 3))} else {low_p}`**


### Distance Error Differences 

Previously, Julian et al (2019) showed that there is a difference in distance error between boundary-dependent and landmark-dependent objects so we ran a paired t-test to replicate these findings in this new participant demographic. 

```{r t-test distance error boundary vs landmark}
distCue_stats <- t.test(subset(relativeInfluenceBlocks, cue=="boundary")$distanceError, 
       subset(relativeInfluenceBlocks, cue=="landmark")$distanceError, paired=TRUE) %>% tidy()

d <- cohen.d(subset(relativeInfluenceBlocks, cue=="boundary")$distanceError, 
       subset(relativeInfluenceBlocks, cue=="landmark")$distanceError, paired=TRUE)

distCue_stats$d <- d$estimate
distCue_stats$dCI_low <- d$conf.int[[1]]
distCue_stats$dCI_high <- d$conf.int[[2]]
```

*Boundary-dependent objects' distance error vs landmark-dependent objects' distance error t-test results:*

t(`r distCue_stats$parameter`)= `r round(distCue_stats$statistic, 2)`, p`r if (distCue_stats$p.value > 0.001) {paste("=", round(distCue_stats$p.value, 3))} else {low_p}`, d=`r round(distCue_stats$d, 2)`, 95% CI [`r round(distCue_stats$dCI_low, 2)`, `r round(distCue_stats$dCI_high, 2)`]


We did not replicate these findings and the lack of difference is evident in the graph below. 

```{r distance error graph}
cue_Dist <- ggplot(relativeInfluenceBlocks, aes(x=cue, y= distanceError)) + 
  # changing labels and title
  scale_x_discrete(labels = c('Boundary', 'Landmark')) +
  labs(x = " ", y = "Distance Error (vm)", title = "Positional Memory") +
  # violin plot
  gghalves::geom_half_violin(data=relativeInfluenceBlocks %>% filter(cue=="landmark"), 
                             position=position_nudge(+0.2), aes(fill=cue),alpha =0.7, color=NA, side="r") +
  gghalves::geom_half_violin(data=relativeInfluenceBlocks %>% filter(cue=="boundary"), 
                             position=position_nudge(-0.2), aes(fill=cue),alpha =0.7, color=NA, side="l") + 
  # scico palette tokyo
  scale_fill_scico_d(palette = 'tokyo', begin=0.15, end=0.85) +
  # single subject data points (1 per participant)
  geom_point(shape=16, size = 1) +
  # line connecting individual participants' values
  geom_line(aes(group=ID), alpha=0.5) +
  # boxplot of distribution (median, 1st and 3rd quartile)
  geom_boxplot(data=relativeInfluenceBlocks %>% filter(cue=="landmark"), 
               position=position_nudge(+0.1), width = .1, outlier.shape = NA) +
  geom_boxplot(data=relativeInfluenceBlocks %>% filter(cue=="boundary"), 
               position=position_nudge(-0.1), width = .1, outlier.shape = NA) +
  # adding plot of mean and SEM  
  stat_summary(data=relativeInfluenceBlocks %>% filter(cue=="landmark"), 
               position=position_nudge(+0.2), fun = mean, geom = "point", size=1, shape = 16, colour = "black") + 
  stat_summary(data=relativeInfluenceBlocks %>% filter(cue=="landmark"), 
               position=position_nudge(+0.2), fun.data = mean_se, geom = "errorbar", colour = "black", width = 0, size = 0.5) +
  stat_summary(data=relativeInfluenceBlocks %>% filter(cue=="boundary"), 
               position=position_nudge(-0.2), fun = mean, geom = "point", size=1, shape = 16, colour = "black") + 
  stat_summary(data=relativeInfluenceBlocks %>% filter(cue=="boundary"), 
               position=position_nudge(-0.2), fun.data = mean_se, geom = "errorbar", colour = "black", width = 0, size = 0.5) +
  # aesthetical changes
  theme_cowplot() +
  theme(legend.position = "none", 
        plot.title = element_text(size=12, lineheight = 1.1), 
        axis.title = element_text(size=12)) +
  # visualizing the significance level of the t-test
  geom_signif(comparisons = list(c("landmark", "boundary")),  test="t.test", 
              test.args=list(alternative = "two.sided", paired=TRUE),
              map_signif_level = TRUE, tip_length = 0, extend_line = 0.045, y_position = 20.1, textsize=2.75)

# saving the graph as pdf and png
ggsave("distancesError.pdf", plot=cue_Dist, 
       units = "cm", width = 15, height = 11, dpi = "retina", device = cairo_pdf, path = here("figures"))
ggsave("distancesError.png", plot=cue_Dist, 
       units = "cm", width = 15, height = 11, dpi = "retina", device = "png", path = here("figures"))

# show the plot
cue_Dist
```

## Miniblocks Learning


### Graphs

The graph below shows the relative influence scores averaged for each miniblock in block 2-4 (averaging over 6 scores for each miniblock)

```{r} 
# necessary summarizing for the graph below
summary_miniblock <- subset_RI %>% 
  group_by(ID, miniblock, cue) %>% 
  summarise(relativeInf = mean(relativeInfluence), 
            riSD = sd(relativeInfluence), 
            cueDis = mean(cueDissonance),
            cdSD = sd(cueDissonance),
            .groups = "drop")

g_mini <- ggplot(summary_miniblock, aes(miniblock, relativeInf, group=interaction(cue, ID), color = cue)) + 
  # assigning scico palette tokyo as a color palette
  scale_color_scico_d(palette = 'tokyo', begin=0.75, end=0.2, labels = c("Landmark", "Boundary")) +
  # connects the mean values for each participant 
  geom_line(size=0.5, alpha = 0.3) +
  # overall mean and se 
  stat_summary(fun=mean, aes(group=cue), geom="point", size=1) +
  stat_summary(fun.data=mean_se, aes(group=cue), geom="errorbar", width=0.1, alpha=0.95) +
  # connects the overall mean to show the improvement
  stat_summary(fun=mean, aes(group=cue), geom="line", size = 0.6) +
  # line showing 0.5 neutral relative score for reference
  geom_hline(yintercept = 0.5, linetype = 2) +
  # changing labels and titles
  labs(x= "Miniblock", y = "Relative Influence (0-1)", subtitle = "Averaged across \nBlocks", title="  ", color = "Cue") +
  # aesthitical changes
  theme_cowplot() +
  # changing limits and breaks on both axis
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_x_continuous(limits = c(0.5, 4.5), breaks = c(1,2,3,4)) +
  theme(axis.title.y = element_blank(), legend.position = "none")

#show the graph
g_mini
```

The graph below shows the relative influence scores for each miniblock throughout block 2-4 (averaging only over 2 scores per miniblock)

```{r}
#necessary summarizing for the graph below
summary_objectTrial <- subset_RI %>%
  group_by(ID, objectTrial, cue) %>% 
  summarise(relativeInf = mean(relativeInfluence), 
            riSD = sd(relativeInfluence), 
            .groups = "drop")

g_objTrial <- ggplot(summary_objectTrial, aes(objectTrial, relativeInf, group=interaction(cue, ID), color=cue)) + 
  # connects the mean values for each participant within each block 
  geom_line(data= subset(summary_objectTrial, objectTrial < 9), size=0.5, alpha = 0.3) +
  geom_line(data= subset(summary_objectTrial, objectTrial < 13 & objectTrial > 8), size=0.5, alpha = 0.3) +
  geom_line(data= subset(summary_objectTrial, objectTrial > 12), size=0.5, alpha = 0.3) +
  # overall mean and se 
  stat_summary(fun=mean, aes(group=cue), geom="point", size=1) +
  stat_summary(fun.data=mean_se, aes(group=cue), geom="errorbar", width=0.1, alpha=0.95) +
  # line connecting the average values within each block
  stat_summary(data = subset(summary_objectTrial, objectTrial < 9), fun=mean, aes(group=cue), geom="line", size = 0.6) +
  stat_summary(data = subset(summary_objectTrial, objectTrial  < 13 & objectTrial > 8), fun=mean, aes(group=cue), geom="line", size = 0.6) +
  stat_summary(data = subset(summary_objectTrial, objectTrial > 12), fun=mean, aes(group=cue), geom="line", size = 0.6) +
  # assigning scico palette tokyo as a color palette
  scale_color_scico_d(palette = 'tokyo', begin=0.75, end=0.2, labels = c("Landmark", "Boundary")) +
  # line showing 0.5 neutral relative score for reference
  geom_hline(yintercept = 0.5, linetype = 2) +
  # adding a vertical lines showing the start of a new block with a proper label
  geom_vline(xintercept = 4.9, alpha = 0.7, linetype=3, size=0.5) +
  annotate("text", label = "Block 2", x = 5.6, y = 1, size = 3) +
  geom_vline(xintercept = 8.9, alpha = 0.7, linetype=3, size=0.5) +
  annotate("text", label = "Block 3", x = 9.6, y = 1, size = 3) +
  geom_vline(xintercept = 12.9, alpha = 0.7, linetype=3, size=0.5) +
  annotate("text", label = "Block 4", x = 13.6, y = 1, size = 3) +
  # changing labels and titles
  labs(x= "Miniblock", y = "Relative Influence (0-1)", subtitle= "Separately per Block", title="Positional Memory", color = "Cue") +
  # changing limits and breaks and its labels of both axis
  scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0,1)) +
  scale_x_continuous(breaks = c(5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16), 
                     labels = c("1", "2", "3", "4", "1", "2", "3", "4", "1", "2", "3", "4")) +
  # aesthetical changes
  theme_cowplot() 

#show the graph
g_objTrial
```

The two graphs created above are composed into a single layout for better, more wholesome visualisation.

```{r}
# specifying the layout
layout <- "
AAAAAA
AAAAAA
AAAAAA
BB####
BB#C##
BB####
"

# assigning a variable for legend
g_leg <- guide_area()

g_min <- g_objTrial + g_mini + g_leg +
  # indicating the layout and gathering the legends
  plot_layout(design = layout, guides = "collect") &
  # unifying aesthetical aspects, mainly text size and style
  theme(axis.title = element_text(size = 10), axis.text = element_text(size=10), 
        legend.title = element_text(size=10), legend.text = element_text(size=10),
        plot.title = element_text(size=12, face="italic"),
        plot.tag = element_text(size = 10, face="bold")) &
  # adding title and tags
  plot_annotation(title = 'Positional Memory',
                  theme = theme(plot.title = element_text(size = 12, face="bold")),
                  tag_levels = list(c('A', 'B')))

# show the assembled graphs
g_min
```

### Miniblock 1 

We noticed that there is a tendency for relative influence score to be above regardless cue-dependency so we wanted to test this statistically so we ran a one-sided, one sample t-test against 0.5.

```{r}
# summarizing by ID for all miniblocks 1 (in block 2-4)
sub_mini_1 <- subset_RI %>%
  filter(miniblock == 1) %>%
  group_by(ID) %>%
  summarise(relInfluence = mean(relativeInfluence), .groups ="drop")

# one-tailed, one sample t-test
mini1_stats <- t.test(sub_mini_1$relInfluence, mu=0.5, alternative = "greater") %>% tidy()

d <- cohen.d(sub_mini_1$relInfluence, f=NA, mu=0.5) 

mini1_stats$d <- d$estimate
mini1_stats$dCI_low <- d$conf.int[[1]]
mini1_stats$dCI_high <- d$conf.int[[2]]
```

*Miniblock 1 RI against 0.5 t-test results:*

t(`r mini1_stats$parameter`)= `r round(mini1_stats$statistic, 2)`, p`r if (mini1_stats$p.value > 0.001) {paste("=", round(mini1_stats$p.value, 3))} else {low_p}`, d=`r round(mini1_stats$d, 2)`, 95% CI [`r round(mini1_stats$dCI_low, 2)`, `r round(mini1_stats$dCI_high, 2)`]


As it seems the relative influence in miniblock is indeed higher than 0.5, therefore they are more likely following boundary as a cue (its old location). Next, we wanted to ensure that there is indeed no difference between the relative influence score between landmark-dependent and boundary-dependent objects in miniblock 1. 

```{r}
# summarizing by ID and cue for all miniblocks 1 (in blocks 2-4)
sub_mini_cue <- subset_RI %>%
  filter(miniblock == 1) %>%
  group_by(ID, cue) %>%
  summarise(relInfluence = mean(relativeInfluence), .groups ="drop")

# two-tailed, paired sample t-test
mini1_cue_stats <- t.test(subset(sub_mini_cue, cue=="landmark")$relInfluence, 
                          subset(sub_mini_cue, cue=="boundary")$relInfluence, paired=TRUE) %>% tidy()

d <- cohen.d(subset(sub_mini_cue, cue=="landmark")$relInfluence, subset(sub_mini_cue, cue=="boundary")$relInfluence, paired=TRUE) 

mini1_cue_stats$d <- d$estimate
mini1_cue_stats$dCI_low <- d$conf.int[[1]]
mini1_cue_stats$dCI_high <- d$conf.int[[2]]
```

*Miniblock 1 landmark-dependent objects' RI against boundary-dependent objects' RI t-test results:*

t(`r mini1_cue_stats$parameter`)= `r round(mini1_cue_stats$statistic, 2)`, p`r if (mini1_cue_stats$p.value > 0.001) {paste("=", round(mini1_cue_stats$p.value, 3))} else {low_p}`, d=`r round(mini1_cue_stats$d, 2)`, 95% CI [`r round(mini1_cue_stats$dCI_low, 2)`, `r round(mini1_cue_stats$dCI_high, 2)`]

HOWEVER!
```{r}
#one sample t-test comparing miniblock 1 relative influence scores to 0.5 for landmark objects
mini1_landmark_stats <- t.test(subset(sub_mini_cue, cue=="landmark")$relInfluence, mu=0.5) %>% tidy()

d <- cohen.d(subset(sub_mini_cue, cue=="landmark")$relInfluence, f=NA, mu=0.5) 

mini1_landmark_stats$d <- d$estimate
mini1_landmark_stats$dCI_low <- d$conf.int[[1]]
mini1_landmark_stats$dCI_high <- d$conf.int[[2]]
```

t(`r mini1_landmark_stats$parameter`)= `r round(mini1_landmark_stats$statistic, 2)`, p`r if (mini1_landmark_stats$p.value > 0.001) {paste("=", round(mini1_landmark_stats$p.value, 3))} else {low_p}`, d=`r round(mini1_landmark_stats$d, 2)`, 95% CI [`r round(mini1_landmark_stats$dCI_low, 2)`, `r round(mini1_landmark_stats$dCI_high, 2)`]

```{r}
#one sample t-test comparing miniblock 1 relative influence scores to 0.5 for boundary objects
mini1_boundary_stats <- t.test(subset(sub_mini_cue, cue=="boundary")$relInfluence, mu=0.5) %>% tidy()

d <- cohen.d(subset(sub_mini_cue, cue=="boundary")$relInfluence, f=NA, mu=0.5) 

mini1_boundary_stats$d <- d$estimate
mini1_boundary_stats$dCI_low <- d$conf.int[[1]]
mini1_boundary_stats$dCI_high <- d$conf.int[[2]]
```

t(`r mini1_boundary_stats$parameter`)= `r round(mini1_boundary_stats$statistic, 2)`, p`r if (mini1_boundary_stats$p.value > 0.001) {paste("=", round(mini1_boundary_stats$p.value, 3))} else {low_p}`, d=`r round(mini1_boundary_stats$d, 2)`, 95% CI [`r round(mini1_boundary_stats$dCI_low, 2)`, `r round(mini1_boundary_stats$dCI_high, 2)`]



### Mixed Models

**Relative Influence**

To test the learning throughout a block, we ran mixed effect model with interaction between cue and miniblock (centered) and added interaction between cue and miniblock as a random slope.

```{r}
formulaMiniblocksCue <- "relativeInfluence ~ cueMM*mini + (1 + cueMM : mini | ID)"
modelMiniblocksCue <- lme4::lmer(formula = formulaMiniblocksCue, data=subset_RI)

tab_model(modelMiniblocksCue, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Cue", "Miniblocks", "Interaction"),  
          dv.labels = "Relative Influence", 
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 
```

To test the significance of the interaction, we ran a likelihood ratio test comparing our model and a model with both cue and miniblock as predictors but without the interaction.

```{r}
#control model for interaction
formulaMiniblocksControl <- "relativeInfluence ~ cueMM+mini + (1 + cueMM : mini | ID)"
modelMiniblocksControl <- lme4::lmer(formula = formulaMiniblocksControl, data=subset_RI)

#likelihood ratio test
ratioMini <- anova(modelMiniblocksCue, modelMiniblocksControl) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioMini$statistic[2], 3)`, p`r if (ratioMini$p.value[2] > 0.001) {paste("=", round(ratioMini$p.value[2], 3))} else {low_p}`**



**Cue specific analysis**

To check whether miniblocks are a significant predictor without the cue we ran a model and likelihood ratio test separately for landmark-dependent and boundary-dependent objects.

```{r}
#landmark-dependent objects 
formulaMiniblocks <- "relativeInfluence ~ mini + (1+mini|ID)"
modelMiniblocksLandmark <- lme4::lmer(formula = formulaMiniblocks, data=subset(subset_RI, cue=="landmark"))

#control model 
formulaMiniControl <- "relativeInfluence ~ 1 + (1+mini|ID)" 
modelMiniLandmarkControl <- lme4::lmer(formula = formulaMiniControl, data=subset(subset_RI, cue=="landmark"))

#likelihood ratio test
ratioMiniLandmark <- anova(modelMiniblocksLandmark, modelMiniLandmarkControl) %>% tidy()
```
 
 **$\chi^{2}$(1) = `r round(ratioMiniLandmark$statistic[2], 3)`, p`r if (ratioMiniLandmark$p.value[2] > 0.001) {paste("=", round(ratioMiniLandmark$p.value[2], 3))} else {low_p}`**


```{r}
# boundary-dependent objects
formulaMiniblocks <- "relativeInfluence ~ mini + (1+mini|ID)"
modelMiniblocksBoundary <- lme4::lmer(formula = formulaMiniblocks, data=subset(subset_RI,cue=="boundary"))

#control model 
formulaMiniControl <- "relativeAngle ~ 1 + (1+mini|ID)" 
modelMiniBoundaryControl <- lme4::lmer(formula = formulaMiniControl, data=subset(subset_RI, cue=="boundary"))

#likelihood ratio test
ratioMiniBoundary <- anova(modelMiniblocksBoundary, modelMiniBoundaryControl) %>% tidy()
```

 **$\chi^{2}$(1) = `r round(ratioMiniBoundary$statistic[2], 3)`, p`r if (ratioMiniBoundary$p.value[2] > 0.001) {paste("=", round(ratioMiniBoundary$p.value[2], 3))} else {low_p}`**


```{r}
#cue specific models table
tab_model(modelMiniblocksLandmark, modelMiniblocksBoundary, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Miniblock"),  
          dv.labels = c("Landmark-dependent", "Boundary-dependent"), 
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 
```


**Cue Dissonance**

As we decided to recode relative influence score to dCorrect / (dCorrect + dOther), we ran the main model with miniblocks again with the new dependent variable to see if the slope differ despite the same direction of improvement. Random effects could not included interaction as this caused singular fit.

```{r}
#model with new recoded dependent variable - cue dissonance
formulaCueDis_mini <- "cueDissonance ~ cueMM*mini + (1+cueMM+mini|ID)"
modelCueDis_mini <- lme4::lmer(formula = formulaCueDis_mini, data=subset_RI)

tab_model(modelCueDis_mini, 
          show.p = FALSE, show.se = TRUE, show.icc = FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Cue", "Miniblock", "Interaction"),  
          dv.labels = "Cue Dissonance", 
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 
```

To test the significance of the interaction, we ran a likelihood ratio test comparing our model and a model with both cue and miniblock as predictors but without the interaction.

```{r}
#control model for interaction
formulaCueDis_miniControl <- "cueDissonance ~ cueMM+mini + (1+cueMM+mini|ID)"
modelCueDis_miniControl <- lme4::lmer(formula = formulaCueDis_miniControl, data=subset_RI)

#likelihood ratio test
ratioCueDis_mini <- anova(modelCueDis_mini, modelCueDis_miniControl) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioCueDis_mini$statistic[2], 3)`, p`r if (ratioCueDis_mini$p.value[2] > 0.001) {paste("=", round(ratioCueDis_mini$p.value[2], 3))} else {low_p}`**


**Graphs**

```{r}
CueDis_miniblock <- ggplot(summary_miniblock, aes(miniblock, cueDis, color=cue)) + 
  theme_cowplot() +
  geom_point(data=subset(summary_miniblock, cue=="boundary"), 
             aes(x = as.numeric(miniblock)-.07), colour = '#845777',
             position = position_jitter(width=0.05), alpha=0.7) + 
  geom_point(data=subset(summary_miniblock, cue=="landmark"), 
             aes(x = as.numeric(miniblock)+.07), colour = '#99C095',
             position = position_jitter(width=0.05), alpha=0.7) + 
  scale_color_scico_d(palette = 'tokyo', begin=0.8, end=0.2) +
  stat_summary(fun=mean, aes(group=cue), geom="line", size = 1.5) +
  stat_summary(fun=mean, data=subset(summary_miniblock, cue=="boundary"), aes(group=cue), 
               geom="point", size = 2, position = position_nudge(x=-.02)) +
  stat_summary(fun.data=mean_se, data=subset(summary_miniblock, cue=="boundary"), aes(group=cue), 
               geom="errorbar", size=0.8, width=0.1, alpha=0.95, position = position_nudge(x=-.02)) +
  stat_summary(fun=mean, data=subset(summary_miniblock, cue=="landmark"), aes(group=cue), 
               geom="point", size = 2, position = position_nudge(x=+.02)) +
  stat_summary(fun.data=mean_se, data=subset(summary_miniblock, cue=="landmark"), aes(group=cue), 
               geom="errorbar", size=0.8, width=0.1, alpha=0.95, position = position_nudge(x=+.02)) +
  scale_x_continuous(breaks = c(1,2,3,4)) +
  scale_y_continuous(limits = c(0.1, 0.9), breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)) +
  labs(x= "Miniblock", y = "Cue Dissonance (0-1)", 
       title="Positional Memory", subtitle = "Data", color="Cue") +
  geom_hline(yintercept = 0.5, linetype=2, alpha=0.6) +
  theme(legend.position = "none")
  
CueDis_miniblock
```

The graph below visualizes the cue dissonance miniblock-dependent improvement based on a mixed model predictions.

```{r}
CueDis_predict <- ggeffects::ggpredict(modelCueDis_mini, terms = c("mini", "cueMM")) %>%
  as_tibble() %>%
  mutate(cuePredict = factor(if_else(group == 1, true = "boundary", false = "landmark"),
                      levels = c("boundary", "landmark")))
  
CueDis_miniModel <- ggplot(CueDis_predict, aes(x = x, y = predicted, colour = cuePredict, fill = cuePredict)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, linetype=0) +
  geom_line(size = 0.5) +
  scale_color_scico_d(palette = 'tokyo', begin=0.2, end=0.8, labels = c("Boundary", "Landmark")) +
  scale_fill_scico_d(palette = 'tokyo', begin=0.2, end=0.8, labels = c("Boundary", "Landmark")) +
  scale_x_continuous(breaks = sort(unique(Sum_all$mini)), labels = c("1", "2", "3", "4")) +
  scale_y_continuous(breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), limits = c(0.1, 0.9)) +
  theme_cowplot() +
  labs(x="Miniblock", y=" ", color="Cue", fill="Cue", 
       subtitle = "Mixed Model", title=" ") + 
  theme(legend.position = "none") +
  geom_hline(yintercept = 0.5, linetype=2, alpha=0.6)

CueDis_miniModel
```


**Explorative**

Follow up t-tests

```{r}
#miniblock 1
m1_cueDis <- t.test(subset(summary_miniblock, cue=="landmark" & miniblock==1)$cueDis, 
                    subset(summary_miniblock, cue=="boundary" & miniblock==1)$cueDis, paired = TRUE) %>% tidy()

d <- cohen.d(subset(summary_miniblock, cue=="landmark" & miniblock==1)$cueDis, 
             subset(summary_miniblock, cue=="boundary" & miniblock==1)$cueDis, paired = TRUE) 

m1_cueDis$d <- d$estimate
m1_cueDis$dCI_low <- d$conf.int[[1]]
m1_cueDis$dCI_high <- d$conf.int[[2]]

#miniblock 2
m2_cueDis <- t.test(subset(summary_miniblock, cue=="landmark" & miniblock==2)$cueDis, 
                    subset(summary_miniblock, cue=="boundary" & miniblock==2)$cueDis, paired = TRUE) %>% tidy()

d <- cohen.d(subset(summary_miniblock, cue=="landmark" & miniblock==2)$cueDis, 
             subset(summary_miniblock, cue=="boundary" & miniblock==2)$cueDis, paired = TRUE) 

m2_cueDis$d <- d$estimate
m2_cueDis$dCI_low <- d$conf.int[[1]]
m2_cueDis$dCI_high <- d$conf.int[[2]]

#miniblock 3
m3_cueDis <- t.test(subset(summary_miniblock, cue=="landmark" & miniblock==3)$cueDis, 
                    subset(summary_miniblock, cue=="boundary" & miniblock==3)$cueDis, paired = TRUE) %>% tidy()

d <- cohen.d(subset(summary_miniblock, cue=="landmark" & miniblock==3)$cueDis, 
             subset(summary_miniblock, cue=="boundary" & miniblock==3)$cueDis, paired = TRUE) 

m3_cueDis$d <- d$estimate
m3_cueDis$dCI_low <- d$conf.int[[1]]
m3_cueDis$dCI_high <- d$conf.int[[2]]

#miniblock 4
m4_cueDis <- t.test(subset(summary_miniblock, cue=="landmark" & miniblock==4)$cueDis, 
                    subset(summary_miniblock, cue=="boundary" & miniblock==4)$cueDis, paired = TRUE) %>% tidy()

d <- cohen.d(subset(summary_miniblock, cue=="landmark" & miniblock==4)$cueDis, 
             subset(summary_miniblock, cue=="boundary" & miniblock==4)$cueDis, paired = TRUE) 

m4_cueDis$d <- d$estimate
m4_cueDis$dCI_low <- d$conf.int[[1]]
m4_cueDis$dCI_high <- d$conf.int[[2]]

```

*miniblock 1:*
t(`r m1_cueDis$parameter`)= `r round(m1_cueDis$statistic, 2)`, p`r if (m1_cueDis$p.value > 0.001) {paste("=", round(m1_cueDis$p.value, 3))} else {low_p}`, d=`r round(m1_cueDis$d, 2)`, 95% CI [`r round(m1_cueDis$dCI_low, 2)`, `r round(m1_cueDis$dCI_high, 2)`]

*miniblock 2:*
t(`r m2_cueDis$parameter`)= `r round(m2_cueDis$statistic, 2)`, p`r if (m2_cueDis$p.value > 0.001) {paste("=", round(m2_cueDis$p.value, 3))} else {low_p}`, d=`r round(m2_cueDis$d, 2)`, 95% CI [`r round(m2_cueDis$dCI_low, 2)`, `r round(m2_cueDis$dCI_high, 2)`]

*miniblock 3:*
t(`r m3_cueDis$parameter`)= `r round(m3_cueDis$statistic, 2)`, p`r if (m3_cueDis$p.value > 0.001) {paste("=", round(m3_cueDis$p.value, 3))} else {low_p}`, d=`r round(m3_cueDis$d, 2)`, 95% CI [`r round(m3_cueDis$dCI_low, 2)`, `r round(m3_cueDis$dCI_high, 2)`]

*miniblock 4:*
t(`r m4_cueDis$parameter`)= `r round(m4_cueDis$statistic, 2)`, p`r if (m4_cueDis$p.value > 0.001) {paste("=", round(m4_cueDis$p.value, 3))} else {low_p}`, d=`r round(m4_cueDis$d, 2)`, 95% CI [`r round(m4_cueDis$dCI_low, 2)`, `r round(m4_cueDis$dCI_high, 2)`]



To see whether the model including cue is better than a miniblock alone with random effect we ran a likelihood ratio test.

```{r}
#control model
formulaJustMini <- "cueDissonance ~ mini + (1+cueMM+mini|ID)"
modelJustMini <- lme4::lmer(formula = formulaJustMini, data=subset_RI)

#likelihood ratio test
ratioMini <- anova(modelCueDis_miniControl, modelJustMini) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioMini$statistic[2],3)`, p`r if (ratioCueDis_mini$p.value[2] > 0.001) {paste("=", round(ratioCueDis_mini$p.value[2], 3))} else {low_p}`**



## Age

To test our main hypothesis, we ran mixed model including age and cue as main predictors with interaction.

### Relative Influence

**Mixed Model**

As our initial dependent variable, we examine these two predictors (cue, age) first to relative influence scores.

```{r}
#full model
formulaFull <- "relativeInfluence ~ age_c*cueMM + ( 1 + cueMM | ID)" 
modelFull <- lme4::lmer(formula = formulaFull, data=subset_RI, REML = FALSE)

#table
tab_model(modelFull, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Age", "Cue", "Interaction"),  
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 

```

The significance of the interaction was tested using likelihood ratio test. 

```{r} 
#control model
controlFinalInt <- "relativeInfluence ~ age_c + cueMM + (1 + cueMM | ID)" 
modelControl <- lme4::lmer(formula = controlFinalInt, data=subset_RI)

#likelihood ratio test
ratioFullModel <- anova(modelFull, modelControl) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioFullModel$statistic[2],3)`, p`r if (ratioFullModel$p.value[2] > 0.001) {paste("=", round(ratioFullModel$p.value[2], 3))} else {low_p}`**



**Cue specific analysis**

To see if age remains a significant predictor without cue, we ran mixed models separately for boundary-dependent and landmark-dependent objects and tested them with likelihood ratio test including only random intercepts for participants.

```{r age model landmark}
#landmark-dependent objects
formulaAgeLandmark <- "relativeInfluence ~ age_c + (1|ID)"
modelAgeLandmark <- lme4::lmer(formula = formulaAgeLandmark, data=subset(subset_RI, cue=="landmark"))

#control model
controlAgeLandmark <- "relativeInfluence ~ 1 + (1 |ID)"
modelControlAgeLandmark <- lme4::lmer(formula = controlAgeLandmark, data=subset(subset_RI, cue=="landmark"))

#likelihood ratio test
ratioAgeLandmark <- anova(modelAgeLandmark, modelControlAgeLandmark) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioAgeLandmark$statistic[2], 3)`, p`r if (ratioAgeLandmark$p.value[2] > 0.001) {paste("=", round(ratioAgeLandmark$p.value[2], 3))} else {low_p}`**


```{r age model boundary}
#boundary-dependent objects
formulaAgeBoundary <- "relativeInfluence ~ age_c +(1|ID)"
modelAgeBoundary <- lme4::lmer(formula = formulaAgeBoundary, data=subset(subset_RI, cue=="boundary"))

#control model
controlAgeBoundary <- "relativeInfluence ~ 1 + (1 |ID)"
modelControlAgeBoundary <- lme4::lmer(formula = controlAgeBoundary, data=subset(subset_RI, cue=="boundary"))

#likelihood ratio test 
ratioAgeBoundary <- anova(modelAgeBoundary, modelControlAgeBoundary) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioAgeBoundary$statistic[2],3)`, p`r if (ratioAgeBoundary$p.value[2] > 0.001) {paste("=", round(ratioAgeBoundary$p.value[2], 3))} else {low_p}`**


```{r}
tab_model(modelAgeLandmark, modelAgeBoundary, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Age"), 
          dv.labels = c("Landmark-dependent", "Boundary-dependent"), 
          string.ci = "Conf. Int (95%)",  
          string.se = "SE",
          CSS = css_theme("cells")) 
```



**Graphs**

The graph below visualizes how the relative influence improves with age as seen in collected data.

```{r}
RI_final <- ggplot(relativeInfluenceBlocks, aes(age, relativeInf, color=cue)) + 
  # setting up color palette - scico tokyo 
  scale_color_scico_d(palette = 'tokyo', begin=0.8, end=0.2, guide = FALSE) +
  # overall mean and se
  stat_summary(fun=mean, aes(group=cue), geom="point", size = 2) +
  stat_summary(fun.data=mean_se, aes(group=cue),  
               geom="errorbar", size=0.8, width=0.1, alpha=0.95) +
  # line connecting the avergae values
  stat_summary(fun=mean, aes(group=cue), geom="line", size = 1.5) +
  # setting up a new color scale for better visibility of individual geom_points
  new_scale_color() + 
  # single  subject data points (1 per participant)
  geom_point(aes(color=cue)) + 
  # new color scale - also scico tokyo but in smaller range
  scale_color_scico_d(palette = 'tokyo', begin=0.7, end=0.3, labels = c("Landmark", "Boundary")) +
  # 0.5 neutral score for reference
  geom_hline(yintercept = 0.5, linetype=2, alpha=0.6) +
  # chaning breaks and limits of both axis
  scale_x_continuous(breaks = c(8,9,10,11,12,13,14,15)) +
  scale_y_continuous(limits = c(0.2, 0.8), breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)) +
  # changing labels and title
  labs(x= "Age", y = "Relative Influence (0-1)", 
       title= "Positional Memory", subtitle = "Data", color="Cue") +
  # background setting
  theme_cowplot() +
  theme(legend.position = "none")

# show the graph
RI_final
```

The graph below visualizes the relative influence age-dependent improvement based on a mixed model predictions.

```{r}
# calculating values predicted by the mixed model
RI_predict <- ggeffects::ggpredict(modelFull, terms = c("age_c", "cueMM")) %>%
  as_tibble() %>%
  mutate(cuePredict = factor(if_else(group == 1, true = "boundary", false = "landmark"),
                      levels = c("boundary", "landmark")))
 
RI_model <- ggplot(RI_predict, aes(x = x, y = predicted, colour = cuePredict, fill = cuePredict)) +
  # plotting the prediction
  geom_line(size = 0.5) +
  # plotting the confidence levels
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, linetype=0) +
  # setting up color and fill palette - scico tokyo 
  scale_color_scico_d(palette = 'tokyo', begin=0.2, end=0.8, labels = c("Boundary", "Landmark")) +
  scale_fill_scico_d(palette = 'tokyo', begin=0.2, end=0.8, labels = c("Boundary", "Landmark")) +
  # changing limits, breaks and labels of both axis 
  scale_x_continuous(breaks = sort(unique(Sum_all$age_c)), labels = c("8", "9", "10", "11", "12", "13", "14", "15")) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8), limits = c(0.2, 0.8)) +
  # background setting
  theme_cowplot() +
  # changing labels and title
  labs(x="Age", y=" ", color="Cue", fill="Cue", 
       subtitle = "Mixed Model", title="  ") + 
  # 0.5 neutral score for reference
  geom_hline(yintercept = 0.5, linetype=2, alpha=0.6) +
  theme(legend.position = "none")

#show the graph
RI_model
```



### Cue dissonance

**Mixed Model**

Next, we tested whether the effect of age and age and cue interaction remain when using the new variable - cue dissonance (one direction recoded relative influence score) as dependent variable. 

```{r}
formulaCueDis <- "cueDissonance ~ age_c*cueMM + ( 1 + cueMM | ID)" 
modelCueDis <- lme4::lmer(formula = formulaCueDis, data=subset_RI)

tab_model(modelCueDis, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE, 
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Age", "Cue", "Interaction"),  
          dv.labels = "Relative Influence", 
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 
```

```{r} 
#control model for interaction
controlCueDis <- "cueDissonance ~ age_c + cueMM + (1 + cueMM | ID)" 
modelControlCueDis <- lme4::lmer(formula = controlCueDis, data=subset_RI)

#likelihood ratio test
ratioCueDis <- anova(modelCueDis, modelControlCueDis) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioCueDis$statistic[2],3)`, p`r if (ratioCueDis$p.value[2] > 0.001) {paste("=", round(ratioCueDis$p.value[2], 3))} else {low_p}`**



**Explorative**

Is cue even significant predictor?

```{r} 
#control model for cue as predictor
controlCueDis_cue <- "cueDissonance ~ age_c + (1 + cueMM | ID)" 
modelCueDis_cueControl <- lme4::lmer(formula = controlCueDis_cue, data=subset_RI)

#likelihood ratio test
ratioCueDis_cue <- anova(modelCueDis_cueControl, modelControlCueDis) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioCueDis_cue$statistic[2],3)`, p`r if (ratioCueDis_cue$p.value[2] > 0.001) {paste("=", round(ratioCueDis_cue$p.value[2], 3))} else {low_p}`**


Adding miniblock as a predictor instead to find the best model.

```{r} 
#control model for miniblock as predictor
miniFullCueDis<- "cueDissonance ~ age_c + mini + (1 + cueMM | ID)" 
modelCueDis_miniFull <- lme4::lmer(formula = miniFullCueDis, data=subset_RI)

tab_model(modelCueDis_miniFull, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Age", "Miniblock"),  
          dv.labels = "Relative Influence", 
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 

#likelihood ratio test
ratioCueDis_miniFull <- anova(modelCueDis_miniFull, modelCueDis_cueControl) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioCueDis_miniFull$statistic[2],3)`, p`r if (ratioCueDis_miniFull$p.value[2] > 0.001) {paste("=", round(ratioCueDis_miniFull$p.value[2], 3))} else {low_p}`**



**Graphs**

The graph below visualizes how the cue dissonance improves with age as seen in collected data.

```{r}
CueDis_final <- ggplot(relativeInfluenceBlocks, aes(age, cueDis, color=cue)) + 
  theme_cowplot() +
  scale_color_scico_d(palette = 'tokyo', begin=0.8, end=0.2, guide = FALSE) +
  stat_summary(fun=mean, aes(group=cue), geom="line", size = 1.5) +
  stat_summary(fun=mean, aes(group=cue), geom="point", size = 2) +
  stat_summary(fun.data=mean_se, aes(group=cue),  
               geom="errorbar", size=0.8, width=0.1, alpha=0.95) +
  new_scale_color() + 
  geom_point(aes(color=cue)) + 
  scale_color_scico_d(palette = 'tokyo', begin=0.7, end=0.3, labels = c("Landmark", "Boundary")) +
  scale_x_continuous(breaks = c(8,9,10,11,12,13,14,15)) +
  scale_y_continuous(limits = c(0.2, 0.8), breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)) +
  labs(x= "Age", y = "Cue Dissonance (0-1)", 
       title="Positional Memory", subtitle = "Data", color="Cue") +
  geom_hline(yintercept = 0.5, linetype=2, alpha=0.6) +
  theme(legend.position = "none")
  
CueDis_final
```

The graph below visualizes the cue dissonance age-dependent improvement based on a mixed model predictions.

```{r}
CueDis_predict <- ggeffects::ggpredict(modelCueDis, terms = c("age_c", "cueMM")) %>%
  as_tibble() %>%
  mutate(cuePredict = factor(if_else(group == 1, true = "boundary", false = "landmark"),
                      levels = c("boundary", "landmark")))
  
CueDis_model <- ggplot(CueDis_predict, aes(x = x, y = predicted, colour = cuePredict, fill = cuePredict)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, linetype=0) +
  geom_line(size = 0.5) +
  scale_color_scico_d(palette = 'tokyo', begin=0.2, end=0.8, labels = c("Boundary", "Landmark")) +
  scale_fill_scico_d(palette = 'tokyo', begin=0.2, end=0.8, labels = c("Boundary", "Landmark")) +
  scale_x_continuous(breaks = sort(unique(Sum_all$age_c)), labels = c("8", "9", "10", "11", "12", "13", "14", "15")) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8), limits = c(0.2, 0.8)) +
  theme_cowplot() +
  labs(x="Age", y=" ", color="Cue", fill="Cue", 
       subtitle = "Mixed Model", title=" ") + 
  theme(legend.position = "none") +
  geom_hline(yintercept = 0.5, linetype=2, alpha=0.6)

CueDis_model
```


### Distance error

**Mixed Model**

To see if age and cue can predict raw distance error, we ran the same analysis as above but with error in virtual meters as a dependent variable.

```{r}
formulaFullDist <- "error ~ age_c*cueMM + ( 1 + cueMM | ID)" 
modelFullDist <- lme4::lmer(formula = formulaFullDist, data=subset_RI)
summary(modelFullDist)

tab_model(modelFullDist, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Age", "Cue", "Interaction"),  
          dv.labels = "Distance Error", 
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 

```

```{r} 
#control model for interaction
controlFullDist<- "error ~ age_c + cueMM + (1 + cueMM | ID)" 
modelControlFullDist <- lme4::lmer(formula = controlFullDist, data=subset_RI)

#likelihood ratio test
ratioFullDist <- anova(modelFullDist, modelControlFullDist) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioFullDist$statistic[2],3)`, p`r if (ratioFullDist$p.value[2] > 0.001) {paste("=", round(ratioFullDist$p.value[2], 3))} else {low_p}`**

**Cue-specific analysis**

To see if age remains a significant predictor without cue, we ran mixed models separately for boundary-dependent and landmark-dependent objects and tested them with likelihood ratio test including only random intercepts for participants.

```{r}
#landmark-dependent objects
formulaAgeLandmark <- "error ~ age_c + (1|ID)"
modelAgeLandmark_error <- lme4::lmer(formula = formulaAgeLandmark, data=subset(subset_RI, cue=="landmark"))

#control model
controlAgeLandmark <- "error ~ 1 + (1 |ID)"
modelControlAgeLandmark_error <- lme4::lmer(formula = controlAgeLandmark, data=subset(subset_RI, cue=="landmark"))

#likelihood ratio test
ratioAgeLandmark <- anova(modelAgeLandmark_error, modelControlAgeLandmark_error) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioAgeLandmark$statistic[2], 3)`, p`r if (ratioAgeLandmark$p.value[2] > 0.001) {paste("=", round(ratioAgeLandmark$p.value[2], 3))} else {low_p}`**


```{r}
#boundary-dependent objects
formulaAgeBoundary <- "error ~ age_c +(1|ID)"
modelAgeBoundary_error <- lme4::lmer(formula = formulaAgeBoundary, data=subset(subset_RI, cue=="boundary"))

#control model
controlAgeBoundary <- "error ~ 1 + (1 |ID)"
modelControlAgeBoundary_error <- lme4::lmer(formula = controlAgeBoundary, data=subset(subset_RI, cue=="boundary"))

#likelihood ratio test 
ratioAgeBoundary <- anova(modelAgeBoundary_error, modelControlAgeBoundary_error) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioAgeBoundary$statistic[2],3)`, p`r if (ratioAgeBoundary$p.value[2] > 0.001) {paste("=", round(ratioAgeBoundary$p.value[2], 3))} else {low_p}`**


```{r}
tab_model(modelAgeLandmark_error, modelAgeBoundary_error, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Age"), 
          dv.labels = c("Landmark-dependent", "Boundary-dependent"), 
          string.ci = "Conf. Int (95%)",  
          string.se = "SE",
          CSS = css_theme("cells")) 
```


**Explorative** 

Is cue even significant predictor?

```{r} 
#control model for cue as predictor
controlFullDist<- "error ~ age_c + (1 + cueMM | ID)" 
modelControlFullDist <- lme4::lmer(formula = controlFullDist, data=subset_RI)

#likelihood ratio test
ratioAgeDist <- anova(modelFullDist, modelControlFullDist) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioAgeDist$statistic[2],3)`, p`r if (ratioAgeDist$p.value[2] > 0.001) {paste("=", round(ratioAgeDist$p.value[2], 3))} else {low_p}`**



Adding miniblock instead of cue a predictor.

```{r} 
#control model for miniblock as predictor
miniFullDist<- "error ~ age_c + mini + (1 + cueMM | ID)" 
modelMiniFullDist <- lme4::lmer(formula = miniFullDist, data=subset_RI)

tab_model(modelMiniFullDist, 
          show.p = FALSE, show.se=TRUE, show.icc=FALSE,
          digits = 4, digits.re = 4,
          pred.labels = c("Intercept", "Age", "Miniblock"),  
          dv.labels = "Relative Influence", 
          string.ci = "Conf. Int (95%)", 
          string.se = "SE",
          CSS = css_theme("cells")) 


#likelihood ratio test
ratioFullMiniDist <- anova(modelMiniFullDist, modelControlFullDist) %>% tidy()
```

**$\chi^{2}$(1) = `r round(ratioFullMiniDist$statistic[2],3)`, p`r if (ratioFullMiniDist$p.value[2] > 0.001) {paste("=", round(ratioFullMiniDist$p.value[2], 3))} else {low_p}`**



**Graphs**

```{r}
distance_final <- ggplot(relativeInfluenceBlocks, aes(age, distanceError, color=cue)) + 
  theme_cowplot() +
  scale_color_scico_d(palette = 'tokyo', begin=0.2, end=0.8, guide = FALSE) +
  stat_summary(fun=mean, aes(group=cue), geom="line", size = 1.5) +
  stat_summary(fun=mean, aes(group=cue), geom="point", size = 2) +
  stat_summary(fun.data=mean_se, aes(group=cue),  
               geom="errorbar", size=0.8, width=0.1, alpha=0.95) +
  new_scale_color() + 
  geom_point(aes(color=cue)) + 
  scale_color_scico_d(palette = 'tokyo', begin=0.3, end=0.7, labels = c("Boundary", "Landmark")) +
  scale_x_continuous(breaks = c(8,9,10,11,12,13,14,15)) +
  labs(x= "Age", y = "Distance error (vm)", 
       subtitle = "Data", title= "Positional Memory", color="Cue") +
  theme(legend.position = "none")
  
distance_final
```


```{r}
distance_predict <- ggeffects::ggpredict(modelFullDist, terms = c("age_c", "cueMM")) %>%
  as_tibble() %>%
  mutate(cuePredict = factor(if_else(group == 1, true = "boundary", false = "landmark"),
                      levels = c("boundary", "landmark")))
  
distance_model <- ggplot(distance_predict, aes(x = x, y = predicted, colour = cuePredict, fill = cuePredict)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, linetype=0) +
  geom_line(size = 0.5) +
  scale_color_scico_d(palette = 'tokyo', begin=0.2, end=0.8, labels = c("Boundary", "Landmark")) +
  scale_fill_scico_d(palette = 'tokyo', begin=0.2, end=0.8, labels = c("Boundary", "Landmark")) +
  scale_x_continuous(breaks = sort(unique(Sum_all$age_c)), labels = c("8", "9", "10", "11", "12", "13", "14", "15")) +
  theme_cowplot() +
  labs(x="Age", y=" ", color="Cue", fill="Cue", 
       subtitle = "Mixed Model") + 
  theme(legend.position = "none") 

distance_model
```


